---
title: "trendEcon"
output:
  flexdashboard::flex_dashboard:
    css: docs.css
    theme: united
    vertical_layout: scroll
    orientation: rows
    social: ["menu"]
    navbar:
      - {icon: "fa-github", 
         title: "Data", 
         href: "https://github.com/trendecon/data", align: right, target: blank}
      - {title: "R package", href: "https://trendecon.github.io/trendecon/", align: right, target: blank}
    includes:
       in_header: v_Script.html
---

```{r setup, include=FALSE}
library(dygraphs)
library(xts)
library(tsbox)
library(dplyr)
library(readr)
library(htmlwidgets)

today <- as.character(Sys.Date())
events <- readr::read_csv("event_data/events.csv")
#Functions to compare years with dygraph
#the axis label is passed as a date, this function outputs only the month of the date
getMonth <- 'function(d){
               var monthNames = ["Jan", "Feb", "Mar", "Apr", "May", "Jun","Jul", "Aug", "Sep", "Oct", "Nov", "Dec"];
               return monthNames[d.getMonth()];
               }'

#the x values are passed as milliseconds, turn them into a date and extract month and day
getMonthDay <- 'function(d) {
                var monthNames = ["Jan", "Feb", "Mar", "Apr", "May", "Jun","Jul", "Aug", "Sep", "Oct", "Nov", "Dec"];
                date = new Date(d);
                return monthNames[date.getMonth()] + " " +date.getDate(); }'

```

<!----------------------------------------------------------------------->
<!---------------------------------------------------------- HOME PAGE -->
<!----------------------------------------------------------------------->

# <font size="3">Home</font> {data-icon="fa-home"}

### trendEcon

#### This website provides daily economic indicators based on Google searches in Switzerland.

How does the Swiss economy develop on a daily basis? Under the extraordinary circumstances caused by the Covid-19 pandemic, the economy is changing faster than usual but standard economic indicators cannot capture this. Indicators such as consumer sentiment index, GDP, or private consumption become available with a lag of up to several months.

As a solution, we provide a set of economic indicators for Switzerland based on Google search trends. These indicators are updated daily and provide policymakers and business leaders with timely information about the Swiss economy. Here you find more information on [how to use our indicators](#background) and you can download the [data](https://github.com/trendecon/data){target="_blank"}.

## Row {.tabset .tabset-fade}

### Perceived Economic Situation (daily)

```{r main_index}

trendecon_all_sa <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

dygraph(trendecon_all_sa,group = "keywords")%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("value", label = "Index") %>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r main_index_monthly}

data_monthly <- trendecon_all_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Perceived Economic Situation` = data_monthly
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The indicator for *Perceived Economic Situation* includes search terms that reflect people’s worries about the economy. For instance, people then google “economic crisis” (Wirtschaftskrise).

###### Keywords

- wirtschaftskrise
- kurzarbeit
- arbeitslos
- insolvenz

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv){target="_blank"}

## Row {.tabset .tabset-fade}

### Watches and Jewellery (daily)
```{r luxury}
luxury_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/luxury_sa.csv",index.column = 1))

dygraph(luxury_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r luxury_monthly}

dm_luxury_sa <- luxury_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Watches and Jewellery` = dm_luxury_sa
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The category *Watches and Jewellery* includes stores and brands selling luxurious watches and jewellery goods and related, more general search terms for luxury consumer goods.

###### Keywords

- christ
- bucherer
- uhren
- uhr
- swarovski
- rhomberg
- juwelier

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/luxury_sa.csv){target="_blank"}

## Row {.tabset .tabset-fade}

### Mobility (daily)

```{r mobility}
mobility_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/mobility_sa.csv",index.column = 1))

dygraph(mobility_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r mobility_monthly}

dm_mobility_sa <- mobility_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Mobility` = dm_mobility_sa
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The category *Mobility* includes search terms related to ground transportation: For instance, checking the railway schedule or calling a taxi.

###### Keywords

- Fahrplan
- taxi
- sixt
- google maps

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/mobility_sa.csv){target="_blank"}

## Row {.tabset .tabset-fade}

### Travel Abroad (daily)
```{r travel}
travel_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/travel_sa.csv",index.column = 1))

dygraph(travel_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r travel_monthly}

dm_travel_sa <- travel_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Travel Abroad` = dm_travel_sa
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The category *Travel Abroad* includes search terms used to book flights and holidays.

###### Keywords

- städtetrip
- flug buchen
- günstige flüge

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/travel_sa.csv){target="_blank"}

## Row {.tabset .tabset-fade}

### Cultural Events (daily)

```{r social}
social_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/social_sa.csv",index.column = 1))

dygraph(social_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r social_monthly}

dm_social_sa <- social_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Cultural Events` = dm_social_sa
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The category *Cultural Events* includes search terms related to concerts, theatres, cinema and ticket providers for such events.

###### Keywords

- kino
- theater
- cinema
- ticketcorner
- starticket
- oper
- konzert

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/social_sa.csv){target="_blank"}

## Row {.tabset .tabset-fade}

### Gardening and Home Improvement (daily)

```{r garden}
garden_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/garden_sa.csv",index.column = 1))

dygraph(garden_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r garden_monthly}

dm_garden_sa <- garden_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Gardening and Home Improvement` = dm_garden_sa
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The category *Gardening and Home Improvement* includes stores selling materials for home improvement such as building materials, garden accessories and electrical supplies.

###### Keywords

- Heim+Hobby
- Bau+Hobby
- Do it Migros
- Jumbo
- Landi
- Gartencenter
- Bauhaus

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/garden_sa.csv){target="_blank"}

## Row {.tabset .tabset-fade}

### Home Office (daily)

```{r home_office}
home_office_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/homeoffice_sa.csv",index.column = 1))

dygraph(home_office_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r home_office_monthly}

dm_home_office_sa <- home_office_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Home Office` = dm_home_office_sa
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The category *Home Office* combine Google inquiries related to the new normal of working from home. The working-from-home-index contains the search terms:

###### Keywords

- headset
- monitor
- maus
- hdmi

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/homeoffice_sa.csv){target="_blank"}


## Row {.tabset .tabset-fade}

### Clothing and Shoes (daily)

```{r clothing}
clothing_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/clothing_sa.csv",index.column = 1))

dygraph(clothing_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r clothing monthly}

dm_clothing_sa <- clothing_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Clothing and Shoes` = dm_clothing_sa
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The category *Clothing and Shoes* includes clothing and shoe stores as well as a general search terms related to buying clothes and shoes. We found that people directly google for the brands they like. Note: the searchword “zalando” was not included because Zalando was not available in Switzerland before 2011.

###### Keywords

- mango
- zara
- H&M
- PKZ
- blue tomato
- dosenbach
- schuhe kaufen
- ochsner schuhe

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/clothing_sa.csv){target="_blank"}

## Row {.tabset .tabset-fade}

### Food Delivery (daily)

```{r fd}
fd_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/fooddelivery_sa.csv",index.column = 1))

dygraph(fd_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent(events$date, events$event, labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r fd_monthly}

dm_fd_sa <- fd_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Food Delivery` = dm_fd_sa
)) %>%
  dyRangeSelector()
```


### Info

###### Description

The category *Food Delivery* includes search terms related to take away and ordering pizza.

###### Keywords

- take away
- takeaway
- pizza bestellen
- dieci pizza

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/fooddelivery_sa.csv){target="_blank"}

## News {.sidebar data-width=310}

##### Latest News
- ###### *New indicators*

  Perceived economic situation for:
  
  + [Austria](#austria)
  
  + [Germany](#germany)

- _08.01.2021_ : New blog post

  + [The home office employee's best companion](#english)
  
  + [Des Homeoffice-Arbeiters bester Freund](#deutsch)


- ###### *trendEcon on TV:*

  + [TV interview](https://www.rsi.ch/la1/programmi/informazione/tempi-moderni/i-servizi/Come-va-l%E2%80%99economia-te-lo-dice-Google-13429910.html){target="_blank"} on RSI LA1.
  + Sehen Sie das [Interview](https://www.rsi.ch/la1/programmi/informazione/tempi-moderni/i-servizi/Come-va-l%E2%80%99economia-te-lo-dice-Google-13429910.html){target="_blank"} mit trendEcon im TV auf RSI LA1.
  
  
- _01.12.2020_ : New blog post

  + [A new indicator for the home office situation and what it has to do with Black Friday](#english)
  
  + [Ein neuer Indikator zur Homeoffice-Situation und was dieser mit Black Friday zu tun hat](#deutsch)


- _23.11.2020_ : [Republik: Die Fieberkurven der Corona-Rezession](https://www.republik.ch/2020/11/23/die-fieberkurven-der-corona-rezession){target="_blank"}.

- _05.11.2020_ : [Finanz und Wirtschaft: Die Schweiz fährt etwas herunter und bestellt wieder Pizza](https://www.fuw.ch/article/die-schweiz-faehrt-etwas-herunter-und-bestellt-wieder-pizza/){target="_blank"}.

- _28.10.2020_ : [Tages Anzeiger: Der Konsum bricht wegen Corona ein](https://www.tagesanzeiger.ch/der-konsum-bricht-wegen-corona-ein-107545280598){target="_blank"}.

- _21.10.2020_ : New blog post

  + [How do Swiss consumers cope with masks? A view on online and on-site shopping](#english)
  
  + [Wie kommen Schweizer Konsumenten mit den Masken zurecht? Eine Sicht auf online und on-site Shopping](#deutsch)

- _18.09.2020_ : New blog post

  + [Football is back! But what about the fans?](#english)
  
  + [Der Ball rollt wieder – Werden Fans live dabei sein?](#deutsch)

- _03.09.2020_ : New blog post

  + [Culinary consumption patterns before, during and after the lockdown: Will the changes remain?](#english)
  
  + [Kulinarische Konsummuster vor, während und nach dem Lockdown: Veränderungen, die bleiben?](#deutsch)
  
- _02.09.2020_ : New blog post

  + [Back to normal or permanent shifts in demand?](#english)
  
  + [Zurück zur Normalität oder dauerhafte Veränderung der Nachfrage?](#deutsch)
  
- _26.08.2020_ : New blog post

  + [Still a long way to go](#english)
  
  + [Ein weiter Weg](#deutsch)

- _24.08.2020_ : New blog post

  + [Large events will be allowed soon – but will people show up?](#english)
  
  + [Grossveranstaltungen werden bald erlaubt sein - aber werden die Leute auch kommen?](#deutsch)

- _08.07.2020_ : [Finanz und Wirtschaft](https://www.fuw.ch/article/die-zweite-welle-laesst-die-konsumenten-kalt/){target="_blank"} article.

- _29.06.2020_ : [Working paper](https://drive.google.com/file/d/12ssYVfF0Kdp0pQXZgFtKetGJmGGH2KEd/view?usp=sharing){target="_blank"}: Constructing Daily Economic Sentiment Indices Based on Google Trends.

- _22.06.2020_ : [Google-anfragen für die Konjunkturanalyse](https://drive.google.com/file/d/1ZpqYkj4FisaiAgewQuQB0TiorNlFdo2T/view?usp=sharing){target="_blank"}. Article in [Schlaglichter der Wirtschaftspolitik](https://www.bmwi.de/Redaktion/DE/Publikationen/Schlaglichter-der-Wirtschaftspolitik/schlaglichter-der-wirtschaftspolitik-07-2020.html){target="_blank"} - Bundesministerium für Wirtschaf und Energie.

- _08.06.2020_ : [Republik](https://www.republik.ch/2020/06/08/seismografie-der-krise){target="_blank"} article.

- _08.06.2020_ : [Ökonomenstimme](https://www.oekonomenstimme.org/artikel/2020/06/trendecon-google-suchanfragen-als-hoffnungstraeger-fuer-die-konjunkturanalyse/){target="_blank"} article.

- _02.06.2020_ : New section [Blog](#deutsch) on the website.

- _29.05.2020_ : [Awardee](https://milano-r.github.io/erum2020-covidr-contest/trendecon.html){target="_blank"} at the eRum2020::CovidR contest.

- _22.05.2020_ : [R package](https://trendecon.github.io/trendecon/){target="_blank"} released.

- _18.05.2020_ : [NZZ](https://www.nzz.ch/wirtschaft/corona-krise-wie-die-lockerungsmassnahmen-wirken-ld.1556075){target="_blank"} article.

- _18.05.2020_ : [Makronom](https://makronom.de/trendecon-google-suchanfragen-als-hoffnungstraeger-fuer-die-konjunkturanalyse-35945){target="_blank"} article.

- _08.05.2020_ : [KOF Bulletin](https://kof.ethz.ch/en/news-and-events/news/kof-bulletin/kof-bulletin/2020/05/trendecon-taegliche-wirtschaftsindikatoren-basierend-auf-schweizer-google-suchtrends.html){target="_blank"} article.

- _08.05.2020_ : trendEcon is 1 out of 16 projects receiving [funding](https://www.versusvirus.ch/funding){target="_blank"} from #versusvirus hackathon. We are thankful for the financial support to keep the project alive.

<!----------------------------------------------------------------------->
<!---------------------------------------------------- BACKGROUND PAGE -->
<!----------------------------------------------------------------------->
# <font size="3">Background</font> {data-icon="fa-info-circle"}

#### **The problem: we lack timely economic data**

Official economic statistics are usually released with a considerable lag. For example, the consumer sentiment index, GDP, or private consumption data become available with a lag of up to several months. The pace at which economic conditions are currently changing, however, requires more timely economic indicators in order to monitor and forecast economic activity. Economists have come up with different innovative ways to monitor the economy based on daily data, e.g. using daily [electricity consumption](https://www.nytimes.com/interactive/2020/04/08/upshot/electricity-usage-predict-coronavirus-recession.html){target="_blank"}.

#### **Our solution: indicators based on Google Trends**

To provide a set of timely economic indicators, we source [Google Trends](https://trends.google.de/trends/?geo=CH){target="_blank"} data. These indicators are available on a daily basis. The idea is that people’s searches on Google tell a lot about their perception of the state of the economy and demand for certain products and services.

When people become unemployed or fear they might lose their job, for example, they start searching for words like "arbeitslos" (unemployed). When people want to buy clothes, they likely type the name of fashion stores like “H&M” or “Zara”. Changes in these searches will then tell us something about unemployment or the demand for clothing.

These indicators provide insights about the abrupt economic changes we are currently experiencing. They will likely be among the first to capture changes in consumption once measures to fight the spread of Covid-19 are lifted step by step. They will thus help to monitor the recovery and possibly indicate lasting changes in consumption habits.

Our main indicator on the *Perceived Economic Situation* captures macroeconomic fluctuations. The other indicators focus on private consumption because i) of its overall importance for economic growth: private consumption makes up over [50% of Swiss GDP](https://www.bfs.admin.ch/bfs/en/home/statistics/national-economy/national-accounts/gross-domestic-product.assetdetail.9546409.html){target="_blank"}; ii) in this crisis, private consumption is hit hardest: due to closures of restaurants, stores, cinemas etc. private consumption is severely limited. This situation is very different to a financial crisis like the one that occurred in 2008/2009 and mainly hit the supply side of the Swiss economy.

#### **How accurate are these indicators?**

To ensure that our combinations of keywords lead to meaningful results, we compare our indicators to existing measures, namely the consumer sentiment index, GDP, and components of private consumption expenditure whenever they provide a meaningful comparison. Our indicators broadly coincide with existing economic time series over the past 13 years, including the recession in 2009. However, note that our indicators do not attempt to replicate or replace any existing time series.

The figure below shows how our main indicator on the perceived economic situation compares to [quarterly GDP](https://www.seco.admin.ch/seco/de/home/wirtschaftslage---wirtschaftspolitik/Wirtschaftslage/bip-quartalsschaetzungen-/daten.html){target="_blank"} growth in Switzerland and the [consumer confidence index](https://www.seco.admin.ch/seco/de/home/wirtschaftslage---wirtschaftspolitik/Wirtschaftslage/Konsumentenstimmung.html){target="_blank"}. For comparison, we have aggregated our indicator to quarters. In this figure, the last observation of our indicators is based on Google searches from January to March 2020, the first quarter of the year. This explains why the drop looks less dramatic than when looking at daily data.

## Row

### {}
```{r seco_comparisson}
target <-
  dataseries::ds("ch_seco_gdp.sa.real.gdp", "xts") %>%
  ts_tbl() %>%
  ts_pc() %>%
  ts_span(2007)
target2 <-
  dataseries::ds("ch_seco_css.i63_index", "xts") %>%
  ts_tbl() %>%
  # ts_pc() %>%
  ts_span(2007)
target2$value <- target2$value/10 # rescale consumer sentiment
target3 <-
  dataseries::ds("ch_seco_css.i12_econ_exp", "xts") %>%
  ts_tbl() %>%
  # ts_pc() %>%
  ts_span(2007)
target3$value <- target3$value/100 # rescale consumer sentiment

data <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv") %>%
  select(time,value) %>%
  ts_frequency("quarter")

ts_dygraphs(ts_c(
  `Perceived Economic Situation` = data,
  `GDP growth` = target,
  `Consumer Sentiment` = target2
)) %>%
  dySeries("Perceived Economic Situation", strokeWidth=3) %>%
  dySeries("GDP growth", strokePattern = "dashed") %>%
  dySeries("Consumer Sentiment", strokePattern = "dotted") %>%
  dyAxis("x", drawGrid = FALSE) %>%
  dyRangeSelector()

```

## Row

### {style="border: 0px; background: none"}

For some indicators, such as *Cultural Events* -- which includes demand for restaurants, cinemas, concerts etc. -- or *Gardening and Home Improvement* (aka do-it-yourself articles), there is no preexisting, well-established indicator to compare our search-based indicators with. Nevertheless these indicators appear meaningful, as we are observing substantial changes in searches for these goods and services compared to normal times. These indicators will therefore provide valuable information on whether the economy is going back to normal as lock-down measures are lifted. In the beginning, some people, especially people in risk groups, may still be be reluctant to go, for example, to restaurants or stroll around shopping malls because they are afraid of contracting the virus.

## Row

### Cultural Events
```{r ce_background, echo = FALSE}
data <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/social_sa.csv") %>%
  ts_span(2019)

# %>%
#   ts_frequency("quarter")

ts_dygraphs(ts_c(
  `Social Consumption` = data
)) %>%
  dySeries("value", label = "Cultural Events") %>%
  dyAxis("x", drawGrid = FALSE) %>%
  dyRangeSelector()

```

## Row

### Gardening and Home Improvement
```{r ghi_background, echo = FALSE}
data <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/garden_sa.csv") %>%
  ts_span(2019)

# %>%
#   ts_frequency("quarter")

ts_dygraphs(ts_c(
  `Gardening` = data
))%>%
  dySeries("value", label = "Gardening and Home Improvement") %>%
  dyAxis("x", drawGrid = FALSE) %>%
  dyRangeSelector()

```

<br>

## Row {.tabset .tabset-fade}

#### **Limitations**

The relationship between these search-based indicators and economic activity seems apparent. We believe that these indicators will provide useful during the whole economic roller-coaster ride that lies ahead of us, during the current downturn as well as the upswing(s) when things go slowly back to (a new?) normal.

Note however, that the relationship between Google searches for specific keywords and real economic activity may change over time. First, the popularity of specific internet platforms and online stores can change, and in that case Google searches as well as actual consumption behavior will change too.

Second, this crisis is very different to previous ones as private demand drops largely because of mandated closures of restaurants, cinemas and stores to fight the spread of Covid-19.

Third, the crisis itself might lead to permanent changes in search behavior. For example, containment measures may lead to a permanent increase of the proportion of the population doing grocery shopping online. While there are currently two major supermarkets offering online shopping, people might start to search more and more for other shops offering this service.

<br><br><br><br>

<!----------------------------------------------------------------------->
<!----------------------------------------------------BLOG PAGE DEUTSCH-->
<!----------------------------------------------------------------------->

# <font size="3">Deutsch</font> {data-navmenu="Blog"}

## Navigation {.sidebar}

- [Background](#background)

- [Method](#method)

- [Blog in English.](#english)

- ------


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 9-->
<!----------------------------------------------------------------------->

## article_9_de

### {style="border: 0px; background: none"}

#### **Des Homeoffice-Arbeiters bester Freund**

<font size="2">8. Januar 2021</font><br>
<font size="2">Alexander Götz</font>

Der Konsum vermag viele Bedürfnisse zu befriedigen. Doch wie sieht es mit Gefühlen der Einsamkeit aus? Die Pandemie fordert verminderte Mobilität und den Rückzug in die eigenen vier Wände, wo die Homeoffices spärlich besetzt sind. Zahlen von Tierheimen dokumentieren einen vermehrtes Interesse am Erwerb von Haustieren. Die Gratiszeitung 20 Minuten berichtete von einer Befragung einzelner Tierheime, nach welcher die Nachfrage nach Hunden und Katzen stark zugenommen habe [(20 Minuten).](https://www.20min.ch/story/die-leute-kompensierten-mit-einem-neuen-buesi-oder-hund-ihre-einsamkeit-332588381409){target="_blank"} Zu Beginn des neuen Jahres 2021 belegt die NZZ diese Beobachtung mit Anmeldezahlen in Tier-Datenbanken [(NZZ).](https://www.nzz.ch/schweiz/haustiere-boomen-waehrend-der-corona-pandemie-ld.1594752){target="_blank"} Gemäss des Artikels sei die Homeoffice-Empfehlung ursächlich für die stärkere Nachfrage.

Internetsuchanfragen sind in der Lage, diese Entwicklung differenzierter zu betrachten. Blickt man auf den Entwicklung über die letzten fünf Jahre (erste Abbildung), fällt auf, dass das Interesse an den Stichworten «tierheim», «qualipet», und «meerschweinchen» in der Tat zugenommen hat. Es fällt ebenso auf, dass der März 2020 starke Peaks der Suchen «qualipet» und «meerschweinschen» auslöste. Dies könnte daraufhin deuten, dass Schweizer*innen sich eher dem Kleintierhandel zuwandten als Tierheimen. Letztere mussten zu Beginn des Lockdowns schliessen und konnten somit die steigende Nachfrage nur teilweise bedienen.

## Row

### {}
```{r }
#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Creating graphs for article 9 ----
article_9_CH <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_9.csv")

ts_dygraphs(article_9_CH[article_9_CH$id=="qualipet" | article_9_CH$id=="tierheim" | article_9_CH$id=="meerschweinchen",]) %>%
  dyRoller(rollPeriod = 8)%>% 
  dyAxis("y", label = "Hits (index from Google trends)") %>%
  dyAxis("x", drawGrid = FALSE)

```

## Row

### {style="border: 0px; background: none"}

Der NZZ liegen von konkrete Zahlen der Tier-Datenbanken Amicus und Identitas vor. Gemäss deren Erhebungen verzeichnet der aufwärtszeigende Trend von Tieranmeldungen einen überproportionalen Sprung im Jahr 2020. Die Daten von trendEcon in der zweiten Abbildung lassen erkennen, dass insbesondere Kleintiere (wie das Meerschweinchen) in der ersten Phase des Lockdown gefragt waren. Im Vergleich dazu sind die Stichworte «hund kaufen» und «katze kaufen» auch stärker gegoogelt worden, jedoch weniger stark als «meerschweinchen». Nach einem kurzfristigen Rückgang der Nachfrage, sind die Suchanfragen nach Haustieren wieder angestiegen, wobei Katzen sich der grössten Beliebtheit erfreuen.

## Row

### {}
```{r }
#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Creating graphs for article 9 ----

ts_dygraphs(article_9_CH[article_9_CH$id=="hund kaufen" | article_9_CH$id=="katze kaufen" | article_9_CH$id=="meerschweinchen",]) %>%
  dyRoller(rollPeriod = 4)%>%
  dyRangeSelector(dateWindow = c("2020-01-01", "2021-01-01"))%>%
  dyAxis("y", label = "Hits (index from Google trends)") %>%
  dyEvent("2020-2-28", "Declaration of 'Special Situation'", labelLoc = "bottom")%>%
  dyEvent("2020-3-16", "Declaration of 'Extraordinary Situation'", labelLoc = "bottom") %>%
  dyEvent("2020-4-27", "Shutdown Easing Phase 1", labelLoc = "bottom") %>%
  dyEvent("2020-5-11", "Shutdown Easing Phase 2", labelLoc = "bottom") %>%
  dyEvent("2020-6-8", "Shutdown Easing Phase 3", labelLoc = "bottom") %>%
  dyEvent("2020-6-22", "End of 'Extraordinary Situation'", labelLoc = "bottom") %>%
  dyEvent("2020-10-19", "Mask wearing obligation extended", labelLoc = "bottom") %>%
  dyEvent("2020-10-28", "Reinforce containment measures", labelLoc = "bottom") %>%
  dyAxis("x", drawGrid = FALSE)

```

## Row

### {style="border: 0px; background: none"}
Inwiefern Haustiere Teil eines neuen Lifestyles werden bleibt indes ungewiss. Je nach Vorgaben des Bundes und Kantone, könnte der Wunsch nach einem Home-Office-Hund Bestand halten. Im Falle von rückkehrender Normalität durch Impferfolge kann die Behausung eines Haustiers umständlich werden, so dass Tiere an die Heime zurückgegeben werden. Dies hängt jedoch auch von der Frage ab, ob das Homeoffice auch nach der Pandemie erhalten bleiben wird. 



<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 8-->
<!----------------------------------------------------------------------->

## article_8_de

### {style="border: 0px; background: none"}

#### **Ein neuer Indikator zum Homeoffice und was dieser mit Black Friday zu tun hat**

<font size="2">1. Dezember 2020</font><br>
<font size="2">Alexander Götz</font>

Das Homeoffice brachte neue Objekte auf die Einkaufslisten der Konsumentinnen und Konsumenten. Waren die eigenen vier Wände vorher klar fürs Wohnen bestimmt, müssen sie nun auch arbeitstauglich sein. Es ist kein Geheimnis, dass vermehrt Monitore, Anschlusskabel und andere Arbeitsobjekte besorgt werden mussten (siehe z.B. [Bloomberg](https://www.bloomberg.com/news/articles/2020-03-17/pc-monitors-in-short-supply-as-virus-spurs-home-office-buying){target="_blank"}). 

TrendEcon hat auch Google Anfragen rund um den Homeoffice-Alltag zu einem Index zusammengefasst. Der Homeoffice-Index enthält die Suchbgeriffe «headset»,»monitor»,»maus» und »hdmi». Wahrscheinlich haben Sie selbst im Frühling oder Herbst mindestens einen dieser Begriffe gegoogelt. Denn der Index zeigt starke Bewegungen zu den verschiedenen Lockdowns. Im März war der Ausschlag ausgesprochen stark. Nach einem Rückgang im Sommer folgte wieder eine vermehrte Nachfrage nach  Homeoffice Elektronika. 

## Row

### {}
```{r }
#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Creating graphs for article 8 ----

# Home Office Indicator
homeoffice <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/homeoffice_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

homeoffice_2018 <- ts_data.frame(homeoffice["2018/2018-12-01"])%>% 
  mutate(time = as.Date(gsub("2018","2020",time))) %>% 
  ts_xts()

homeoffice_2019 <- ts_data.frame(homeoffice["2019/2019-12-01"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

homeoffice_2020 <- ts_data.frame(homeoffice["2020/2020-21-01"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2018` = homeoffice_2018,
  `2019` = homeoffice_2019,
  `2020` = homeoffice_2020
)) %>%
  dyRoller(rollPeriod = 7)%>% 
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dySeries("2018", strokePattern = "dotdash") %>%
  dySeries("2019", strokePattern = "dashed") %>%
  dySeries("2020", strokePattern = NULL,  strokeWidth = 1.5) %>%
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = " Home Office trendEcon index")


```

## Row

### {style="border: 0px; background: none"}

Der Vergleich mit den Vorjahren zeigt, dass die leichte Baisse im Sommer immer noch über dem Interesse vorheriger Sommer liegt. Interessant ist auch die Beobachtung, dass gegen Ende November in allen dargestellten Jahren die Nachfrage nach Elektronikartikeln zunimmt. Wie kommt es zu diesen jährlichen Ausschlägen Ende November?

Die Antwort ist schnell gefunden: Black Friday! Die Rabattschlacht erfreut seit einigen Jahren auch Herr und Frau Schweizer. Besonders Onlinehändler mischen kräftig mit. Wie sich der Black Friday und die darauf folgende Cyber Week auf das Interesse an Elektronikartikeln und deren Händler, wie Galaxus oder Interdiscount, ausgewirkt haben erfahren Sie im nächsten Blogeintrag.



<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 7-->
<!----------------------------------------------------------------------->

## article_7_de

### {style="border: 0px; background: none"}

#### **Wie kommen Schweizer Konsumenten mit den Masken zurecht? Eine Sicht auf online und on-site Shopping**

<font size="2">21. October 2020</font><br>
<font size="2">Alexander Götz</font>

Die Maskenpflicht in öffentlichen Verkehrsmitteln (6. Juli 2020) und für den Besuch Zürcher Geschäfte (27. August 2020) wurde zu Beginn ihrer Einführung kritisch beäugt, da sie möglicherweise eine erstarkende post-lockdown Konsumnachfrage bremsen könnte. Dieses Phänomen wurde im Aus- und Inland untersucht, wobei die Analysen uneinheitliche Resultate evozieren. Nach der landesweiten Einführung von erhöhten Schutzmassnahmen (19. Oktober) stellt sich die Frage nach möglichen Auswirkungen einer Maskenpflicht noch mehr. Dieser Artikel versucht daher, die Perspektive von Google-Suchenden einzubringen, um die bereits öffentliche Evidenz um eine weitere Facette zu erweitern.

Die Global Economic Recovery Trackers der [Financial Times](https://www.ft.com/content/272354f2-f970-4ae4-a8ae-848c4baf8f4a){target="_blank"}, welche wie die trendEcon-Indikatoren auf hochfrequenten Daten beruhen, implizieren, dass der Einzelhandel in manchen Ländern wieder auf ein gewöhnliches Konsum-Niveau zurückgekehrt ist. Sieht man jedoch die Daten der Ladeneintritte (Retail Footfall) an, fällt auf, dass der on-site Einzelhandel im Jahresvergleich (y/y) zwischen 20% (Italien, Schweden) bis zu 60% (UK, US) zurückhinkt. Ökonomen kommen in einer auf Mobilität-Echtzeitdaten basierenden [Studie](https://www.econstor.eu/bitstream/10419/218945/1/Compulsory_face_masks_Germany_5june2020.pdf){target="_blank"} in Deutschland zum Schluss, dass die gestaffelte Einführung einer Maskenpflicht keine signifikanten Auswirkungen auf die Besuche im Einzelhandel haben. Die Thematik ist auch von hiesigen Medien aufgenommen worden [(NZZ, 17. September 2020)](https://www.nzz.ch/wirtschaft/coronavirus-maskenpflicht-geringe-einbussen-fuer-geschaefte-ld.1576918?mktcid=nled&mktcval=120&kid=nl120_2020-9-18&ga=&trco=){target="_blank"}. Der Artikel argumentiert, dass die strengere Maskenpflicht in Zürich nicht zu Einbussen im Einzelhandel (gemessen in Anzahl Kartentransaktionen) führt, im Vergleich zur Ost- oder Zentralschweiz. Jedoch begrenzt sich die regionale Analyse auf einen Zeitabschnitt zwischen August und September, ohne Vorjahreszahlen einzubeziehen.

Die Daten von trendEcon lassen eine differenzierte Betrachtung von on-site sowie auch online Handel zu. Zuerst lässt sich festhalten, dass der noch neue Begriff "maskenpflicht"ein grosses Interesse sowohl im Kanton wie auch im gesamten Land (gestrichelte Linie) auslöste. Mit dem bundesrätliche Beschluss vom 18. Oktober 2020 hat das Suchverhalten nach "maskenpflicht" einen neuen Rekordwert erreicht. Doch wie hat sich die Maskenpflicht auf die Konsumfreude im stationären Einzelandel ausgewirkt? 

## Row

### {}
```{r masks_0}

article_7_CH <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_7_CH.csv") %>%
  ts_xts()
article_7_ZH <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_7_ZH.csv") %>%
  ts_xts()

ts_dygraphs(ts_c(
  `CH` = article_7_CH$maskenpflicht,
  `ZH` = article_7_ZH$maskenpflicht)) %>%
  dyRoller(rollPeriod = 4)%>% 
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("CH", label = "\"maskenpflicht\" searched in CH") %>%
  dySeries("ZH", label= "\"maskenpflicht\" searched in ZH only", strokePattern = "dashed") %>%
  dyEvent("2020-3-16", "Start Lockdown        ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Reopening - Phase I        ", labelLoc = "top") %>%
  dyEvent("2020-7-6", "Mask Measure CH - Public transport        ", labelLoc = "top") %>% 
  dyEvent("2020-8-27", "Mask Measure ZH - Retail        ", labelLoc = "top") %>% 
  dyEvent("2020-10-19", "Mask Measure CH - Retail        ", labelLoc = "top") %>% 
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {style="border: 0px; background: none"}

Die Suchbegriffe «öffnungszeiten», «shopping center» stehen für Konsumgelegenheiten, die physisch besucht werden. Die folgenden Zeitreihen zeigen das Suchverhalten in der Schweiz und Zürich der letzten zwei Jahren, wobei erkennbar ist, dass sich «Shopping Center»-Suchanfragen nach einem Rückgang während des Lockdowns noch nicht auf ein Vorjahresniveau bewegt haben. Interessant wird sein, welche Auswirkungen die zweite Infektionswelle auf das sonst starke Weihnachtsgeschäft haben wird. Auch sichtbar ist, dass «shopping center» in Zürich weniger gesucht wurde nachdem die Maskenpflicht eingeührt wurde. Nach einer kurzen Aufwärtsentwicklung während im September, hat ein Abwärtstrend eingesetzt, welcher mit den landesweiten Massnahmen zu tun haben könnte.
Der Begriff «öffnungszeiten» lässt sich nicht eindeutig interpretieren. Einerseits könnte man die Reihe so deuten, dass ein Vor-Corona-Niveau erreicht worden ist. Jedoch muss auch beachtet werden, dass der Lockdown nicht zu relativen Rückgängen geführt hat. Auch denkbar ist, dass Googlende vielleicht sicherheitshalber nach Öffnungszeiten suchen, statt vor verschlossen Türen zu stehen. 

## Row

### {}
```{r masks_1}

ts_dygraphs(ts_c(
  `CH_ot` = article_7_CH[,1], 
  `CH_sc` = article_7_CH[,2],
  `ZH_ot` = article_7_ZH[,1],
  `ZH_sc` = article_7_ZH[,2])) %>%
  dyRoller(rollPeriod = 4)%>% 
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("CH_ot", label = "\"öffnungszeiten\" searched in CH") %>%
  dySeries("ZH_ot", label = "\"öffnungszeiten\" searched in ZH", strokePattern = "dashed") %>%
  dySeries("CH_sc", label = "\"shopping center\" searched in CH") %>%
  dySeries("ZH_sc", label = "\"shopping center\" searched in ZH", strokePattern = "dashed") %>%
  dyEvent("2020-3-16", "Start Lockdown        ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Reopening - Phase I        ", labelLoc = "top") %>%
  dyEvent("2020-7-6", "Mask Measure CH - Public transport        ", labelLoc = "top") %>% 
  dyEvent("2020-8-27", "Mask Measure ZH - Retail        ", labelLoc = "top") %>%
  dyEvent("2020-10-19", "Mask Measure CH - Retail       ", labelLoc = "top") %>% 
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)

```

## Row

### {style="border: 0px; background: none"}

In der dritten Abbildung blicken wir auf Aushängeschilder des Online-Handels, namentlich «galaxus», «coop at home» und «le shop». Hierbei fällt auf, dass der E-Commerce-Riese Galaxus seine starke Position während des Lockdowns verbessern konnte. Nach einer temporär explodierenden Nachfrage, hat sich das neue Niveau über Vorjahreswerten eingepegelt. Die Online-Ableger der grössten Retailer der Schweiz Coop und Migros zeigen jedoch, dass dem fulminanter Höhepunkt während des Lockdowns ein Abflachen auf Vorjahresniveau folgte. Die neuen Sicherheitsmassnahmen haben jedoch wieder zu einer erhöhten Nachfrage bei Online-Retailern geführt.

## Row

### {}
```{r masks_2}

ts_dygraphs(ts_c(
  article_7_CH$`coop at home`,
  article_7_CH$`le shop`,
  article_7_CH$galaxus)) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>%
  dyEvent("2020-3-16", "Start Lockdown        ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Reopening - Phase I        ", labelLoc = "top") %>%
  dyEvent("2020-7-6", "Mask Measure CH - Public transport        ", labelLoc = "top") %>% 
  dyEvent("2020-8-27", "Mask Measure ZH - Retail      ", labelLoc = "top") %>%
  dyEvent("2020-10-19", "Mask Measure CH - Retail       ", labelLoc = "top") %>% 
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {style="border: 0px; background: none"}

Die Daten zu Google-Suchanfragen können nicht direkt einen Effekt der Maskenpflicht identifizieren; dennoch indizieren sie eine Verschiebung des Konsumgewohnheiten im Non-Food-Bereich von on-site zu online, was insbesondere durch einen Rückgang bei Food-Onlinehändlern währen des Sommers gezeigt werden kann. Vermehrte Einkäufe von Zuhause in Verbindung mit einer eher rückgängigen Konsumquote implizieren jedoch, dass der on-site Konsum sich nicht vollständig erholt hatte. Der erneute Aufschwund des Online-Konsums deutet darauf hin, dass sich die Schweizer*innen in die Sicherheit der eigenen Stuben begeben statt Geschäfte aufzusuchen.


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 6-->
<!----------------------------------------------------------------------->

## article_6_de

### {style="border: 0px; background: none"}

#### **Der Ball rollt wieder – Werden Fans live dabei sein?**

<font size="2">03. September 2020</font><br>
<font size="2">Alexander Götz</font>

An diesem Wochenende beginnt die neue Fussballsaison in der Schweiz und Deutschland. Aufgrund der Corona-Krise hat die Swiss Football League (SFL) den Spielplan für die Saison 2020/2021 angepasst. Neben terminlichen Verschiebungen kommen dem Fussballfan hierzulande jedoch auch neue Regelungen entgegen, auf welche es sich neu einzustellen gilt. Doch sind die Fans bereit und haben sie ihre Eintrittskarten bereits organisiert?

Bereits im vergangenen Monat hat der Schweizerische Fussballverband an einer Vorlage für ein [Schutzkonzept](https://www.football.ch/portaldata/27/resources/dokumente/diverses/Covid_Schutzkonzept_August2020_DE.pdf){target="_blank"} gearbeitet, wie Fussballvereine ihre Fans Corona-konform zu behandeln haben. Neben individuellen Regeln (nur symptomfrei erscheinen, Abstand halten, Hände waschen) müssen auch Richtlinien eingehalten werden, die im Verantwortungsbereich der Vereine liegen. So dürfen sich z.B. bis Ende Oktober maximal 1000 Personen im Stadion befinden. Gemäss der bundesrätlichen Ankündigung vom 12. August sind ab Oktober grundsätzlich wieder mehr als 1000 Leute bei Grossveranstaltungen zugelassen. Wichtiger aber ist, dass der Schutz der Bürger\*innen und somit auch der Stadiongänger\*innen bei den Kantonen liegt. Weiter kann eine Maskenpflicht auf dem Stadiongelände anfallen, welche wiederum von den unterschiedlichen kantonalen Covid-19-Regeln abhängen. Je nach Kanton und Fussballstadion müssen sich Fans an die regionalen Gegebenheiten anpassen.

Es ist also kompliziert! Wenn wir unseren trendEcon-Indikator für kulturelle Events heranziehen, lässt sich eine Niveauverschiebung seit Beginn des Jahres erkennen. Auffällig ist, dass diese Verschiebung einmalig ist in den letzten vier Jahren. Der Indikator illustriert mithin eine Unsicherheit über den Besuch von Veranstaltungen allgemein. Obwohl Fussball nur entfernt mit kulturellen Events in Verbindung gebracht werden kann, spielt diese Unsicherheit auch bei den Fans eine Rolle.

Die Daten von trendEcon veranschaulichen, dass die Unsicherheit bezüglich eines Stadionbesuchs relativ zu den letzten Jahren gross ist. Die Zeitreihe des Suchbegriffs «Spielplan» lässt ein interessantes Muster erkennen: Während grossen Fussballturnieren (Welt- und Europameisterschaft) schiesst das Suchverhalten hoch, während die Aktivität in der übrigen Zeit konstant bleibt. Nur in diesem Jahr ist das Niveau auf ein noch nie erreichtes Tief gesunken. Wenn man auf den Begriff «Saisonkarte» blickt, zeigt sich ein ähnliches Bild: In jede zweiten Jahreshälfte steigt die Nachfrage nach Saisonkarten. In diesem Jahr gab es einen Absturz dieser Nachfrage, die sich im Schnitt auf einem tieferen Niveau einpendelt. Die Unsicherheit über das diesjährige Stadionglück veranlasste z.B. den Schweizer Meister BSC YB den Jahreskartenverkauf temporär auszusetzen [(BSCYB News)](https://www.bscyb.ch/news?nID=12105){target="_blank"}. Auch solche Massnahmen tragen dazu bei, dass die Tendenz der Saisonkarten-Verkäufe nach unten zeigt.

Wir haben auch einen Blick auf die Suchbegriffe «Fallzahlen» und «Maskenpflicht» geworfen und erkennen klar eine erhöhte Suchaktivität nach den beiden Begriffen. Insbesondere der Begriff «Fallzahlen» erreicht einen neuen Rekordwert, welcher das Level der ersten Infektionswelle im Frühling weit überragt.

Die Daten unserer Analyse verbildlichen die Unsicherheiten von Schweizer Fussballfans. Aufgrund dieser Unsicherheiten und über die zweite Welle und möglichen neuen Restriktionen gehen wir davon aus, dass die Besuchszahlen in Fussballstadien niedrig bleiben werden. Generell handelt es sich um Unsicherheiten, die die Mehrheit der Schweizer\*innen betreffen: Wie entwickelt sich die zweite Welle? Muss eine Maske in der Öffentlichkeit getragen werden? Es sind letztlich Fragen, die sich nicht nur auf den Verkauf von Stadionkarten, sondern auf die generelle Konsumfreude auswirken könnten.

## Row

### {}
```{r football_0}

article_6 <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_6.csv") %>%
  ts_xts()

ts_dygraphs(article_6) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dyOptions(connectSeparatedPoints = TRUE) %>% 
  dySeries("maskenpflicht", strokeWidth = 2, strokePattern = "dashed") %>%
  dySeries("fallzahlen", strokeWidth = 2, strokePattern = "dashed") %>%
  dySeries("spielplan", strokeWidth = 2,drawPoints = FALSE) %>%
  dySeries("saisonkarte", strokeWidth = 2) %>%
  dyEvent("2020-3-16", "Lockdown     ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Phase I - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-5-11", "Phase II - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-6-8", "Phase III - Reopening     ", labelLoc = "top") %>%
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {}
```{r football_1}

# Cultural Event indicator
cultural <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/social_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

cultural_2017 <- ts_data.frame(cultural["2017/2017-09-17"])%>% 
  mutate(time = as.Date(gsub("2017","2020",time))) %>% 
  ts_xts()

cultural_2018 <- ts_data.frame(cultural["2018/2018-09-17"])%>% 
  mutate(time = as.Date(gsub("2018","2020",time))) %>% 
  ts_xts()

cultural_2019 <- ts_data.frame(cultural["2019/2019-09-17"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

cultural_2020 <- ts_data.frame(cultural["2020/2020-09-17"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2017` = cultural_2017,
  `2018` = cultural_2018,
  `2019` = cultural_2019,
  `2020` = cultural_2020
)) %>%
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dySeries("2017", strokePattern = "dashed") %>%
  dySeries("2018", strokePattern = "dotdash") %>%
  dySeries("2019", strokePattern = "dashed") %>%
  dySeries("2020", strokePattern = NULL,  strokeWidth = 1.5) %>%
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = " Cultural Event trendecon index")


```


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 5-->
<!----------------------------------------------------------------------->

## article_5_de

### {style="border: 0px; background: none"}

#### **Kulinarische Konsummuster vor, während und nach dem Lockdown: Veränderungen, die bleiben?**

<font size="2">03. September 2020</font><br>
<font size="2">Alexander Götz</font>

Am 27. August 2020 verkündete das Staatssekretariat für Wirtschaft (SECO) den historischen Rückgang der Schweizer Wirtschaftsleistung während des zweiten Quartals 2020 gegenüber dem Vorquartal um 8.2%. Die Ökonomen des SECO erklären in ihrer [Konjunkturnotiz](https://www.seco.admin.ch/dam/seco/de/dokumente/Wirtschaft/Wirtschaftslage/VIP%20Quartalsschätzungen/konjunkturnotiz_2020_08_27.pdf.download.pdf/konjunkturnotiz_2020_08_27.pdf){target="_blank"}, dass insbesondere der private Konsum einen noch nie dagewesenen Einbruch erlitten hat. In vergangenen Krisen hat sich gezeigt, dass der private Konsum die Wirtschaft vor schlimmeren Entwicklungen, welche zumeist von rückläufige Investitionen angeheizt werden, bewahrt hat. In der gegenwärtigen Krise haben lediglich die Veränderungen der Staatsausgaben sich positiv auf die BIP-Veränderung ausgewirkt. Der Aussenhandel brach ebenso ein, da wichtige Handelspartner der Schweiz auch von Restriktionen betroffen waren. Weil der private Konsum den grössten Anteil aller BIP-Komponenten darstellt, wirken sich dessen Schwankungen besonders stark auf die Wirtschaftsleistung aus. So trägt der Konsumrückgang bedeutend zum BIP-Rückgang bei und konnte folglich seiner Rolle als Garant von Stabilität nicht nachkommen.

Schon seit Ausbruch der Pandemie und während des Lockdowns spekulieren [US-amerikanische Ökonomen](https://www.nber.org/papers/w26949){target="_blank"}, dass die bisherigen Konsumgewohnheiten sich nicht nur kurzfristig sondern auch mittel- und langfristig verändern könnten. Insbesondere die Nutzung von Online-Shops für alltägliche Einkäufe habe durch die Ausgeh-Restriktionen einen weiteren Schub erhalten, welche durchaus eine Zeitenwende im Einzelhandel einläuten könnte. 

Ob sich aber die Zusammensetzung des Konsumkorbs mit den Einkaufsmöglichkeiten, z.B. eben über Online-Shops statt im Supermarkt, verändert, ist eine andere Frage. Ob und wie sich die Nachfrage nach Gütern verändert, lässt sich mit einem Blick auf einzelne Konsumrubriken genauer erforschen. Im Folgenden wollen wir uns Konsumrubriken widmen, die zu den alltäglichsten des Lebens gehören: dem Essen.

Mit trendEcon können wir die Suchanfragen nach spezifischen Konsumgütern, welche mutmasslich durch die Pandemie und dem Lockdown beeinflusst wurden, genauer betrachten. Als Suchbegriffe haben wir die Begriffe «Restaurant» und «Bar» sowie «Rezept» und «Sauerteig» gewählt. 

Das erste Begriffspaar («Restaurant» und «Bar»; gestrichelte Linien) spiegelt Suchanfragen wider, die mit dem Ausgehen zusammenhängen. Betrachten wir den zeitlichen Verlauf der Suchanfragen, fällt auf, dass die beiden Begriffe während des Lockdowns kaum mehr gegoogelt wurden und erst wieder gegen Anfang Juni 2020 das übliche Niveau erlangten. Interessanterweise sehen wir auch, dass der Begriff «Restaurant» nach den Lockerungsphasen sogar stärker gesucht wurde als vor dem Lockdown. Dies kann einerseits ein Kompensationseffekt sein, wobei man sich danach danach sehnte sich bekochen zu lassen anstatt selbst zu kochen. Aber auch eine weit verbreitete Unsicherheit ist denkbar, so dass wir in der Schweiz vor einem Restaurant viel eher nachsehen, ob dieses überhaupt geöffnet ist. In der angesprochenen Konjunkturnotiz berichtet das SECO ebenfalls von Kompensationseffekten im Konsum aus, rechnet aber nicht mit einer vollständigen Kompensation der Ausfälle der ersten Jahreshälfte.

Die anderen Begriffe («Rezept» und «Sauerteig», durchgezogene Linien) stehen für Aktivitäten, die wir mit dem Kochen zuhause in Verbindung bringen. Die Entwicklung der Suchanfrage «Rezept» lässt erkennen, dass es typischerweise während der Festtage im Dezember ins Suchfeld eingegeben wird. Der Lockdown scheint aber aus den Restaurantgänger\*innen Köch\*innen gemacht zu haben. Erstaunlicherweise haben Schweizer\*innen sich auch Zeit für aufwändigere Verfahren wie die Kultivierung von Sauerteigen genommen [(NZZ, Juni 2020)](https://www.nzz.ch/zuerich/sauerteig-eine-ode-an-das-tamagotchi-der-corona-krise-ld.1558248){target="_blank"}.  So dokumentiert die Zeitreihe über das Suchverhalten nach «Sauerteig» einen gewaltigen Hype zwischen März und Mai, der nach den ersten Lockerungen sein jähes Ende fand, was daran liegen könnte, dass Arbeitnehmende ihre Home-Offices wieder verliessen. 

Ein Blick auf den heutigen Stand zeigt, dass die erläuterten Suchbegriffe wieder alte Niveaus erreicht haben. Sorgen über die Auswirkungen der zweiten Infektionswelle oder Jobsicherheit können sich jedoch auch in den kommenden Wochen auf das Konsumverhalten auswirken. Es bleibt also zu beobachten, ob der Konsum im kommenden Quartal die rückläufige Wirtschaftsleistung zu stabilisieren vermag. Wir sind jedoch skeptisch, ob der Sauerteig Teil dieser nahen Zukunft sein wird.

## Row

### {}
```{r culinary}

article_3 <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_3.csv") %>%
  ts_xts()

ts_dygraphs(article_3) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("Restaurant", strokeWidth = 2, strokePattern = "dashed") %>%
  dySeries("Bar", strokeWidth = 2, strokePattern = "dashed") %>%
  dyEvent("2020-3-16", "Lockdown     ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Phase I - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-5-11", "Phase II - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-6-8", "Phase III - Reopening     ", labelLoc = "top") %>%
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 4-->
<!----------------------------------------------------------------------->


## article_4_de

### {style="border: 0px; background: none"}

#### --------------------------------------------

#### **Zurück zur Normalität oder dauerhafte Veränderung der Nachfrage?**

<font size="2">02. September 2020</font><br>
<font size="2">Stefan Legge</font>

Für die Menschen in der Schweiz hat sich das Leben im Frühjahr 2020 dramatisch verändert, als der Bundesrat Mitte März den so genannten Lockdown verkündete. Da die Schweizerinnen und Schweizer nicht mehr in Restaurants, Bars oder Einkaufszentren gehen konnten, fanden sie neue Wege, ihre Freizeit zu geniessen.

Bei den Lebensmitteln standen zwei Aktivitäten im Vordergrund: Brot backen und online Essen bestellen. Erstere war so weit verbreitet, dass derEconomist im Juli [darüber schrieb](https://www.economist.com/leaders/2020/07/09/sourdough-economics-no-need-to-knead){target="_blank"}. Das britische Magazin wies jedoch darauf hin, dass die Menschen, sobald die Pandemie und der wirtschaftliche Abschwung vorbei sind, das Brotbacken den Experten überlassen und sich darauf konzentrieren sollten, das Brot mit ihrer normalen Arbeit zu verdienen. Ähnlich verhält es sich mit anderen Aktivitäten während des Lockdowns. Viele Menschen gingenrasch nach den ersten Lockerungen wieder ins Restaurant anstatt zu Hause zu kochen.

Dies wirft die Frage auf, ob der Covid-19-Schock nur zu kurzfristigen Anpassungen in der Art und Weise führte, wie die Menschen ihre Freizeit verbringen. Oder ist es wirklich so, dass wir (bislang) dauerhafte Veränderungen in der Konsumentennachfrage beobachten?

Mit trendEcon sehen wir, wie sich die Google-Suchfrequenzen in den letzten Wochen, Monaten und Jahren entwickelt haben. Damit können wir prüfen, ob sich die Präferenzen der Schweizer Konsumenten nur vorübergehend oder dauerhaft verschoben haben. In der untenstehenden Abbildung sind die Ergebnisse für die Suchbegriffe "Brot backen", "Essen bestellen", "Netflix" sowie für eine Wortgruppe zum Thema Garten und Heimwerken dargestellt.

## Row

### {}
```{r art_4_0_de}

blog_ar_4 <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_4.csv") %>%
  ts_xts()

ts_dygraphs(blog_ar_4) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dyAxis("x", drawGrid = FALSE) %>% 
  dySeries("Netflix", strokePattern = NULL)%>% 
  dySeries("Essen bestellen", strokePattern = "dashed") %>% 
  dySeries("Brot backen", strokePattern = "dotdash") %>% 
  dyLegend(width = 500) %>% 
  dyHighlight(highlightCircleSize = 3, 
              highlightSeriesBackgroundAlpha = 0.7,
              hideOnMouseOut = TRUE)
```

## Row

### {style="border: 0px; background: none"}

Für einige der Schlüsselbegriffe deuten die Daten auf einen kurzfristigen Boom während des Covid-19 Lockdown hin. Das Interesse am Brotbacken oder an Nahrungsmittellieferungen stieg während der Abriegelung rapide an, brach aber ebenso schnell mit den ersten Lockerungen der Beschränkungen wieder ein. Unterdessen bleibt die Suche nach gartenbezogenen Begriffen im Vergleich zur Zeit vor Corona auf einem leicht erhöhten Niveau. Die Covid-19-Krise hat zu einigen dramatischen Veränderungen im Leben und im Konsumverhalten der Menschen geführt. Es scheint plausibel, dass die Menschen an einigen dieser neuen Gewohnheiten festhalten werden, wie z.B. an der Online-Bestellung von Lebensmitteln oder an der Gartenarbeit in ihrer Freizeit.

Falls dies geschieht, werden Unternehmen in Zukunft mit einer anderen Verbrauchernachfrage konfrontiert sein. Dies hätte dann bedeutende Auswirkungen auf Investitionsentscheidungen. Diese allerdings in Erwartung eines anhaltenden Booms zu treffen, sollte auf einem tieferen Verständnis der Nachfrageverschiebungen basieren. Die Daten von trendEcon helfen dabei, indem sie wertvolle Einblicke in die Vorlieben der Verbraucher bieten.

## Row

### {}
```{r art_4_1_de}

food <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/fooddelivery_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

food_2018 <- ts_data.frame(food["2018/2018-09-01"])%>% 
  mutate(time = as.Date(gsub("2018","2020",time))) %>% 
  ts_xts()

food_2019 <- ts_data.frame(food["2019/2019-09-01"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

food_2020 <- ts_data.frame(food["2020/2020-09-01"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2018` = food_2018,
  `2019` = food_2019,
  `2020` = food_2020
)) %>%
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dySeries("2018", strokePattern = "dotdash") %>%
  dySeries("2019", strokePattern = "dashed") %>%
  dySeries("2020", strokePattern = NULL) %>%
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = "Food delivery trendEcon index")

```

## Row

### {}
```{r art_4_2_de}

garden <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/garden_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

garden_2018 <- ts_data.frame(garden["2018/2018-09-01"])%>% 
  mutate(time = as.Date(gsub("2018","2020",time))) %>% 
  ts_xts()

garden_2019 <- ts_data.frame(garden["2019/2019-09-01"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

garden_2020 <- ts_data.frame(garden["2020/2020-09-01"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2018` = garden_2018,
  `2019` = garden_2019,
  `2020` = garden_2020
)) %>%
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dySeries("2018", strokePattern = "dotdash") %>%
  dySeries("2019", strokePattern = "dashed") %>%
  dySeries("2020", strokePattern = NULL) %>%
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = "Gardening and home improvement trendecon index")

```



<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 3A-->
<!----------------------------------------------------------------------->


## article_3a_de

### {style="border: 0px; background: none"}

#### --------------------------------------------

#### **Ein weiter Weg**

<font size="2">26. August 2020</font><br>
<font size="2">Stefan Legge</font>

Viele der Aufgaben, die die Menschen tagtäglich erledigen müssen, haben sich seit Jahrhunderten nicht verändert: Essen besorgen, einen bequemen Schlafplatz finden, Verletzungen und Krankheiten behandeln oder von einem Ort zum anderen gelangen. Der einflussreiche Wirtschaftstheoretiker Clayton M. Christensen hat auf der Grundlage dieser Tatsache eine Theorie der zu erledigenden Aufgaben ([jobs to be done](https://hbr.org/2016/09/know-your-customers-jobs-to-be-done){target="_blank"} aufgestellt. Seine wichtigste Beobachtung ist, dass sich die Werkzeuge und Verfahren, die die Menschen zur Erledigung dieser Aufgaben einsetzen, viel häufiger ändern als die Aufgaben selbst.

Was die Mobilität betrifft, so wechselten die Menschen ihr primäres Verkehrsmittel immer dann, wenn neue Technologien - Zug, Auto, Flugzeug - es ihnen erlaubten und Anreize dazu boten. In jüngster Zeit wurden wir Zeugen eines weiteren Grundes, warum die Menschen die Art und Weise, wie sie von A nach B kamen, änderten: Die Covid-19-Pandemie machte einige Transportmittel weniger attraktiv. Darüber hinaus reisten viele Menschen aufgrund von Gesundheitsbedenken weit weniger. 

Aktuelle Daten der KOF deuten darauf hin, dass sich die durchschnittlich zurückgelegte Entfernung (veranschaulicht durch den [Mobilitätsindex](https://kofdata.netlify.app/#/keys?dataset=ch.kof.mobind){target="_blank"}) von ihrem Tiefpunkt Ende März weitgehend erholt hat. Dies erlaubt es uns, interessante Fragen zu stellen: Hat die Pandemie zu nachhaltigen Veränderungen bei der Wahl der Verkehrsmittel geführt? Benutzen Menschen weiterhin Fahrräder und Autos statt der öffentlichen Verkehrsmittel?

Daten von trendEcon geben darüber Aufschluss. Wir beobachten, wie sich die Google-Suchfrequenzen in der jüngeren Vergangenheit entwickelt haben und können sie mit den Werten von 2019 oder 2018 vergleichen. So können wir prüfen, ob die Schweizer Bürgerinnen und Bürger ihre Mobilitätspräferenzen nur vorübergehend oder dauerhaft verschoben haben. In der Abbildung unten illustrieren wir die Ergebnisse für die Suchbegriffe "Velo kaufen", "Auto kaufen", "Busticket" sowie "Zugticket". Ausserdem zeigen wir unseren Index für Mobilität zusammen mit jenem der KOF.

Die Daten deuten auf eine deutliche kurzfristige Auswirkung von Covid-19 hin: Das Interesse an Fahrrädern erreichte einen Höhepunkt, während die Suche nach öffentlichen Verkehrsmitteln stark zurückging. Interessanter sind die nachhaltigen Folgen dieses Schocks. Zwar ist die Analyse zum jetzigen Zeitpunkt noch früh - die Pandemie ist nicht vorbei - aber wir sehen weiterhin ein erhöhtes Interesse an Fahrrädern. Es bleibt abzuwarten, ob sich dies in den kommenden Monaten fortsetzt. Auch der negative Schock für die öffentlichen Verkehrsmittel (Busse und Züge) dauert noch an: das Interesse am Öffentlichen Verkehr ist im Vergleich zur Zeit vor Corona deutlich zurückgegangen.

Covid-19 verursachte einige dramatische Veränderungen im Leben der Menschen und in ihren Mobilitätspräferenzen. Die von trendEcon bereitgestellten Daten bieten aktuelle Einblicke in die wichtigsten Mobilitätstrends.

## Row

### {}
```{r art_3a_mob_1_de}

blog_ar_3_a <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_3_a.csv") %>%
  ts_xts()

ts_dygraphs(blog_ar_3_a[,1:2]  %>%
              ts_frequency("month")) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dyAxis("x", drawGrid = FALSE) %>% 
  dySeries("Auto kaufen", strokePattern = "dashed") %>% 
  dyLegend(width = 500) %>% 
  dyHighlight(highlightCircleSize = 3, 
              highlightSeriesBackgroundAlpha = 0.7,
              hideOnMouseOut = TRUE)
```

## Row

### {}
```{r art_3a_mob_2_de}

blog_ar_3_a <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_3_a.csv") %>%
  ts_xts()

ts_dygraphs(blog_ar_3_a[,3:4]  %>%
              ts_frequency("month")) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dyAxis("x", drawGrid = FALSE) %>% 
  dySeries("Zugticket", strokePattern = "dashed") %>% 
  dyLegend(width = 500) %>% 
  dyHighlight(highlightCircleSize = 3, 
              highlightSeriesBackgroundAlpha = 0.7,
              hideOnMouseOut = TRUE)

```

## Row

### {}
```{r art_3a_mob_3_de}

kof_mob <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_3_a_mobility_kof.csv") %>%
  ts_xts()

mobility_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/mobility_sa.csv",index.column = 1))
mobility_trendecon <- as.xts(mobility_sa["2020-01-07/2020-08-24"])
mobility_trendecon_r <- (mobility_trendecon-min(mobility_trendecon))/(max(mobility_trendecon)-min(mobility_trendecon))

mobility <- cbind(kof_mob,mobility_trendecon_r)

ts_dygraphs(mobility) %>%
  dyAxis("x", drawGrid = FALSE)%>%
  dyAxis("y", label = "rescaled index") %>% 
  dySeries("value", label = "KOF mobility index") %>%
  dySeries("mobility_trendecon_r", label = "trendecon mobility index", strokePattern = "dashed") %>%
  dyEvent("2020-3-16", "Lockdown    ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Reopening - Phase I    ", labelLoc = "top") %>%
  dyEvent("2020-5-11", "Reopening - Phase II    ", labelLoc = "top") %>%
  dyEvent("2020-6-8", "Reopening - Phase III    ", labelLoc = "top") %>% 
  dyLegend(width = 500) %>% 
  dyHighlight(highlightCircleSize = 3, 
              highlightSeriesBackgroundAlpha = 0.7,
              hideOnMouseOut = TRUE)

```


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 2-->
<!----------------------------------------------------------------------->

## article_2_de

### {style="border: 0px; background: none"}

#### --------------------------------------------

#### **Grossveranstaltungen werden bald erlaubt sein - aber werden die Leute auch kommen?**

<font size="2">24. August 2020</font><br>
<font size="2">Stefan Legge</font>

Am 12. August 2020 hat der Bundesrat [angekündigt](https://www.srf.ch/news/schweiz/grossanlaesse-masken-kredite-das-hat-der-bundesrat-entschieden){target="_blank"}, dass ab Oktober wieder Grossanlässe mit mehr als tausend Teilnehmenden zugelassen werden. Damit wurden die im März verhängten COVID-19-bezogenen Einschränkungen erneut gelockert. Viele Unternehmen, Sportvereine und Organisatoren von Veranstaltungen waren erleichtert, endlich Licht am Ende des Tunnels zu sehen. 

Aber nur weil Grossveranstaltungen erlaubt sind, heißt das noch lange nicht, dass die Menschen sie auch tatsächlich besuchen werden. Die Zahl der täglich neuen COVID-19-Fälle ist seit Wochen im Aufwärtstrend. Viele - aber nicht alle - Menschen in der Schweiz versuchen nach wie vor, Grossanlässe zu vermeiden. Eine [US-amerikanische](https://www.nber.org/papers/w27650){target="_blank"} Studie zeigt, dass die Wiedereröffnung von Restaurants nach der Schliessung die Kunden glauben lässt, dass es sicher war, wieder auswärts zu essen. In ähnlicher Weise kann das Zulassen von Grossveranstaltungen ein Signal der Sicherheit setzen. Hat die jüngste Ankündigung also Einzelpersonen dazu veranlasst, ihre Meinung zu ändern?

Mithilfe von trendEcon können wir sehen, wie sich die Google-Suchfrequenzen in den vergangenen Tagen, Wochen oder Monaten entwickelt haben. Als Suchbegriffe verwenden wir "Festival", "Tickets kaufen", "Hallenstadion" (eine Mehrzweckanlage in Zürich), "Letzigrund" (Stadion in Zürich), sowie "Konzert".

Für keines der Stichworte deuten die Daten auf eine positive Wirkung der jüngsten Ankündigung hin. Es scheint, dass die Schweizerinnen und Schweizer sich bisher nicht beeilt haben, Veranstaltungen zu finden und Tickets zu kaufen. Für diese verhaltene Reaktion kann es viele Gründe geben: Die Bevölkerung ist nach wie vor besorgt über das Virus (die Zahl der Suchanfragen nach "Corona" oder "Corona Symptomen" bleibt auf hohem Niveau stabil), und die wahrgenommene wirtschaftliche Situation ist nach wie vor schlechter als vor dem Ausbruch der Pandemie Ende Februar. Darüber hinaus zögern die Organisatoren von Grossveranstaltungen immer noch, für 2020 zu planen. Das Hallenstadion Zürich führt derzeit nur sieben Veranstaltungen für den Rest des Jahres auf.

Die kommenden Wochen werden zeigen, ob die Nachfrage nach Grossanlässen steigt, je näher die Schweiz der Wiederaufnahme von Grossanlässen im Oktober kommt. Wenn nicht, wird das Licht am Ende des Tunnels vielleicht doch nicht allzu hell sein.

## Row

### {}
```{r art_2}

article_2 <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_2.csv") %>%
  ts_xts()

ts_dygraphs(article_2) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("Hallenstadion", strokeWidth = 2, strokePattern = "dashed") %>%
  dySeries("Festival",strokeWidth = 1, strokePattern = "dashed") %>%
  dySeries("Konzert",drawPoints = TRUE) %>%
  dyEvent("2020-3-16", "Lockdown     ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Phase I - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-5-11", "Phase II - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-6-8", "Phase III - Reopening     ", labelLoc = "top") %>%
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```
<br><br><br><br>

<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE GERMAN / Article 1-->
<!----------------------------------------------------------------------->

## article_1_de

### {style="border: 0px; background: none"}

#### --------------------------------------------

#### **Wie geht es der Schweizer Wirtschaft heute?**

##### trendEcon bietet neue Erkenntnisse

<font size="2">25. Mai 2020</font><br>

Die erste Jahreshälfte 2020 darf schon jetzt als historisch betrachtet werden. Selten zuvor sind Volkswirtschaften in derart kurzer Zeit so sehr eingebrochen wie jetzt. Infolge von COVID-19 und den diesbezüglichen staatlichen Massnahmen steigen praktisch überall die Arbeitslosenzahlen rapide an. Die wirtschaftliche Leistung gemessen am Bruttoinlandsprodukt (BIP) fällt stärker als wir es seit Jahrzehnten gesehen haben. Nach wie vor herrscht jedoch grosse Unsicherheit darüber, wie dramatisch der wirtschaftliche Einbruch wird und wie rasch sich Volkswirtschaften von der Krise erholen werden.

In der Schweiz ist ein Rückgang des BIP um rund sechs Prozent zu erwarten [(Seco, April 2020)](https://www.seco.admin.ch/seco/de/home/wirtschaftslage---wirtschaftspolitik/Wirtschaftslage/konjunkturprognosen.html){target="_blank"}. Allerdings trifft dies nicht alle Sektoren der Wirtschaft gleichmässig. Restaurants oder auch der Flughafen Zürich sind ungleich härter betroffen als beispielsweise Supermärkte oder die Pharmabranche. Während die Extrema recht offensichtlich sind, bleiben jedoch viele Fragen offen. 

Wie schnell steigt beispielsweise die Nachfrage nach langlebigen Konsumgütern wieder? In Rezessionen sparen Konsumentinnen und Konsumenten insbesondere bei Kleidung, Möbeln oder Autos. Ausgaben in diesen Bereichen lassen sich leichter aufschieben, weshalb diese Branchen sehr pro-zyklisch sind: In der Rezession leiden sie besonders – und mit ihnen die Werbebranche und in nächster Instanz Zeitungen, welche weniger Werbeanzeigen verkaufen. Somit ist die Nachfrage nach Kleidung oder Autos über Zweit- und Drittrundeneffekte auch für viele andere Industrien wichtig.

Sowohl für die Politik als auch für Unternehmen stellt die hohe Unsicherheit ein Problem da. Wie viel staatliche Unterstützung braucht es und wo ist sie am nötigsten? Ab wann können sich Firmen wieder auf steigende Nachfrage und damit Umsätze einstellen?

Daten können uns helfen, solche Fragen besser zu beantworten. Allerdings müssen diese vielfach erst aufbereitet und graphisch veranschaulicht werden. Die von uns neu geschaffene Plattform [trendEcon.org](#home) setzt sich genau dies zum Ziel. Jeden Tag suchen Schweizerinnen und Schweizer auf Google nach unzähligen Begriffen. Via [Google Trends](https://trends.google.de/trends/?geo=CH){target="_blank"} lässt sich für jeden einsehen, welche Begriffe derzeit sehr häufig gesucht werden. Illustrativ ist ein Blick auf die Begriffe «WC Papier» sowie «Rezession»:

## Row

### {}
```{r}
wc_papier_ts <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/wc_papier.csv",index.column = 1))

rezession_ts <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/rezession.csv",index.column = 1))

ts_dygraphs(ts_c(
  `WC Papier` = wc_papier_ts,
  `Rezession` = rezession_ts
)) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("WC Papier", strokePattern = "dashed") %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {style="border: 0px; background: none"}

Es zeigt sich hier anschaulich, wie ab der zweiten Märzwoche die Suchanfragen nach «Rezession» stiegen und viele Menschen Mitte März aufgrund einer kurzfristigen Knappheit an WC-Papier danach im Internet gesucht haben. Die Sorge um das WC-Papier ist rasch verflogen, aber das Thema Rezession ist nach wie vor sehr präsent, wenn auch auf einem tieferen Niveau.

Diese Beispiele verdeutlichen auch einige Probleme: Welche Suchbegriffe sind relevant und auf welche Weise können mehrere Begriffe kombiniert verwendet werden? Wie lassen sich die Daten sauber vergleichbar darstellen: was ist der sinnvolle Vergleichsmassstab?Diese Aspekte versuchen wir mit **trendEcon** zu adressieren, indem wir aus einer Vielzahl an möglichen Suchbegriffen die geeignetsten auswählen und die Daten ab Januar 2006 aufbereiten. Die Datenaufbereitung beinhaltet unter anderem eine saisonale Bereinigung ebenso wie die Berücksichtigung von Feiertagen.

Im Ergebnis zeigt **trendEcon** derzeit neben einem Krisenindex auch für mehrere Branchen die zeitliche Entwicklung auf. Unser Hauptindikator «Perceived Economic Situation» basiert auf den Google Suchanfragen in der Schweiz nach den Stichworten «Wirtschaftskrise», «Kurzarbeit», «arbeitslos» und «Insolvenz». Die darauf basierenden Daten liefern ein Bild davon ab, wie sehr sich die Menschen in der Schweiz um die wirtschaftliche Entwicklung sorgen. Je häufiger nach den vier Begriffen gesucht wird, desto schlechter die Einschätzung der aktuellen Situation. Graphisch zeigt sich deutlich der Einbruch ab Ende Februar und der Tiefpunkt kurz nach den Beschlüssen des Bundesrats vom 16. März 2020:


## Row {.tabset .tabset-fade}

### Perceived Economic Situation (daily)

```{r}

trendecon_all_sa <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

dygraph(trendecon_all_sa,group = "keywords")%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("value", label = "Index") %>%
  dyEvent("2020-3-16", "Lockdown", labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r}

data_monthly <- trendecon_all_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Perceived Economic Situation` = data_monthly
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The indicator for *Perceived Economic Situation* includes search terms that reflect people’s worries about the economy. For instance, people then google “economic crisis” (Wirtschaftskrise).

###### Keywords

- wirtschaftskrise
- kurzarbeit
- arbeitslos
- insolvenz

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv){target="_blank"}

## Row

### {style="border: 0px; background: none"}

Auffällig ist zudem, dass sich die Stimmung bereits wieder deutlich aufgehellt hat – wobei der Indikator nach wie vor unter dem langfristigen Niveau ist. Als sehr geeigneter Vergleich kann man die Daten aus dem Jahr 2019 heranziehen und erkennt, wie markant der Unterschied ist:

## Row

### {}
```{r}
trendecon_all_sa <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

PEI_2019 <- ts_data.frame(trendecon_all_sa["2019/2019-05-25"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

PEI_2020 <- ts_data.frame(trendecon_all_sa["2020/2020-05-25"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2019` = PEI_2019,
  `2020` = PEI_2020
)) %>%
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = "Perceived Economic Situation")
```

## Row

### {style="border: 0px; background: none"}

Neben der gesamtwirtschaftlichen Betrachtung bietet **trendEcon** auch eine Reihe von sektorspezifischen Indikatoren an. Dabei zeigt sich – als Bestätigung für die Qualität der Daten – der starke und anhaltende Einbruch der Reisebranche. Suchanfragen nach «Städtetrip», «Flug buchen» oder «günstige Flüge» sind nach wie vor viel geringer als zu Vor-Corona Zeiten:

## Row {.tabset .tabset-fade}

### Travel Abroad
```{r}
travel_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/travel_sa.csv",index.column = 1))

dygraph(travel_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent("2020-3-16", "Lockdown", labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Info

###### Description

The category *Travel Abroad* includes search terms used to book flights and holidays.

###### Keywords

- städtetrip
- flug buchen
- günstige flüge

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/travel_sa.csv){target="_blank"}

## Row

### {style="border: 0px; background: none"}

Einen ähnlichen und anhalten Einbruch sehen wir bei kulturellen Veranstaltungen. Im Gegensatz dazu ist die Nachfrage nach Essenslieferungen oder auch Baumärkten auf einem (positiven) Rekordstand.

Zusammengefasst lässt sich sagen, dass **trendEcon** eine Plattform für tagesaktuelle Informationen zum Zustand der schweizerischen Wirtschaft bietet. Wir werden in den kommenden Wochen weitere Suchbegriffe und (Sub-) Indikatoren hinzufügen, um das Angebot an Informationen stetig zu vergrössern. Ausserdem testen wir laufend die Nützlichkeit unserer Daten für die Prognose von volkswirtschaftlich relevanten Grössen. Sämtliche Daten sind frei zum [Download](https://github.com/trendecon/data/tree/master/data/) verfügbar und der Code wird bald auf GitHub veröffentlicht.

<!----------------------------------------------------------------------->
<!----------------------------------------------------BLOG PAGE ENGLISH-->
<!----------------------------------------------------------------------->


# <font size="3">English</font> {data-navmenu="Blog"}

## Navigation {.sidebar}

- [Background](#background)

- [Method](#method)

- [Blog auf Deutsch](#deutsch)


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 9-->
<!----------------------------------------------------------------------->

## article_9_en

### {style="border: 0px; background: none"}

#### **The home office employee's best companion**

<font size="2">January 8th, 2021</font><br>
<font size="2">Alexander Götz</font>

Consumption can satisfy many needs. But what about feelings of loneliness? The pandemic calls for reduced mobility and a retreat into one's own four walls, where (home) offices are less crowded. Figures from animal shelters document an increased interest in acquiring pets. The free newspaper 20 Minuten reported from a survey of some animal shelters that dogs and cats' demand has risen sharply during the pandemic [(20 Minuten).](https://www.20min.ch/story/die-leute-kompensierten-mit-einem-neuen-buesi-oder-hund-ihre-einsamkeit-332588381409){target="_blank"} At the beginning of the new year 2021, the NZZ confirms this observation with registration figures from animal databases [(NZZ).](https://www.nzz.ch/schweiz/haustiere-boomen-waehrend-der-corona-pandemie-ld.1594752){target="_blank"} According to the article, the home office recommendation is causal for this higher demand.

Internet search queries enable a more differentiated look at the developments. If one looks at the development over the last five years (first figure), it is noticeable that the interest in the keywords "tierheim" (animal home), "qualipet" (Swiss pet and pet supplies retailer), and "meerschweinchen" (guinea pig) increased, indeed. It also becomes apparent that March 2020 provided strong peaks for the searches "qualipet" and "meerschweinchen". This observation could indicate that the Swiss preferred pet shops instead of animal shelters. This makes sence as the latter had to close due to the COVID19 measures  and were thus only able to serve the increasing demand at the beginning of the lockdown.


## Row

### {}
```{r }
#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Creating graphs for article 9 ----
article_9_CH <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_9.csv")

ts_dygraphs(article_9_CH[article_9_CH$id=="qualipet" | article_9_CH$id=="tierheim" | article_9_CH$id=="meerschweinchen",]) %>%
  dyRoller(rollPeriod = 8)%>% 
  dyAxis("y", label = "Hits (index from Google trends)") %>%
  dyAxis("x", drawGrid = FALSE)

```

## Row

### {style="border: 0px; background: none"}
The NZZ reports concrete figures from the animal databases Amicus and Identitas. According to their numbers, the upward trend among animal registrations also recorded a disproportionate jump upward in 2020. The data from trendEcon in the second figure indicates that in particular small animals (such as the guinea pigs) were in high demand during the first phase of the lockdown. In comparison, the keywords "hund kaufen" (buy dog) and "katze kaufen" (buy cat) were also more popular, but less than "meerschweinchen". After a short-term drop in demand in the Summer, searches for all pets have rebounded, with cats enjoying the most significant popularity.

## Row

### {}
```{r }
#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Creating graphs for article 9 ----

ts_dygraphs(article_9_CH[article_9_CH$id=="hund kaufen" | article_9_CH$id=="katze kaufen" | article_9_CH$id=="meerschweinchen",]) %>%
  dyRoller(rollPeriod = 4)%>%
  dyRangeSelector(dateWindow = c("2020-01-01", "2021-01-01"))%>%
  dyAxis("y", label = "Hits (index from Google trends)") %>%
  dyEvent("2020-2-28", "Declaration of 'Special Situation'", labelLoc = "bottom")%>%
  dyEvent("2020-3-16", "Declaration of 'Extraordinary Situation'", labelLoc = "bottom") %>%
  dyEvent("2020-4-27", "Shutdown Easing Phase 1", labelLoc = "bottom") %>%
  dyEvent("2020-5-11", "Shutdown Easing Phase 2", labelLoc = "bottom") %>%
  dyEvent("2020-6-8", "Shutdown Easing Phase 3", labelLoc = "bottom") %>%
  dyEvent("2020-6-22", "End of 'Extraordinary Situation'", labelLoc = "bottom") %>%
  dyEvent("2020-10-19", "Mask wearing obligation extended", labelLoc = "bottom") %>%
  dyEvent("2020-10-28", "Reinforce containment measures", labelLoc = "bottom") %>%
  dyAxis("x", drawGrid = FALSE)

```

## Row

### {style="border: 0px; background: none"}

To what extent pets are part of the current living standard, however, remains uncertain. Depending on federal and cantonal guidelines, the desire for a home office dog could endure. In the case of returning normality due to vaccination procedure, the housing of a pet may become cumbersome so that employees will return the pets to the animal shelters. However, this also depends on whether home offices will remain after the pandemic. 




<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 8-->
<!----------------------------------------------------------------------->

## article_8_en

### {style="border: 0px; background: none"}

#### **A new indicator for working from home and what Black Friday has to do with it**

<font size="2">December 1st, 2020</font><br>
<font size="2">Alexander Götz</font>

Working from home has brought new objects onto the shopping lists of consumers. While the home was mainly intended for living in before, it must now also be suitable for work. It is no secret that monitors, connection cables and other work objects have been in high demand since spring (see e.g. [Bloomberg](https://www.bloomberg.com/news/articles/2020-03-17/pc-monitors-in-short-supply-as-virus-spurs-home-office-buying){target="_blank"}). 

TrendEcon has also combined Google inquiries related to the new normal of working from home to an index, which reflects an interest in items that make life in the kitchen table office more comfortable. Our working-from-home-index contains the search terms "headset", "monitor", "mouse" and "hdmi". You probably googled at least one of these terms yourself in spring or autumn. The index shows a strong co-movement with the different lockdowns:  in March the uptick in demand was extremely strong. After a decline in summer, demand for home office electronics increased again. 


## Row

### {}
```{r }

#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Creating graphs for article 7 ----
# How do Swiss consumers cope with masks

# Cultural Event indicator
homeoffice <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/homeoffice_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

homeoffice_2018 <- ts_data.frame(homeoffice["2018/2018-12-01"])%>% 
  mutate(time = as.Date(gsub("2018","2020",time))) %>% 
  ts_xts()

homeoffice_2019 <- ts_data.frame(homeoffice["2019/2019-12-01"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

homeoffice_2020 <- ts_data.frame(homeoffice["2020/2020-21-01"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2018` = homeoffice_2018,
  `2019` = homeoffice_2019,
  `2020` = homeoffice_2020
)) %>%
  dyRoller(rollPeriod = 7)%>% 
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dySeries("2018", strokePattern = "dotdash") %>%
  dySeries("2019", strokePattern = "dashed") %>%
  dySeries("2020", strokePattern = NULL,  strokeWidth = 1.5) %>%
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = " Home Office trendEcon index")


```

## Row

### {style="border: 0px; background: none"}

A comparison with previous years shows that despite the slight slump in summer, interest in these items lies still above the level of previous summers. It is also interesting to note that towards the end of November, demand for electronic goods increased in all the years shown. What causes these annual swings at the end of November?

Short answer: Black Friday! The discount battle been delighting Swiss consumers for a few years now. In the next blog, you can read about how Black Friday and the Cyber Week that followed impacted the demand for electronic goods and their retailers, such as Galaxus or Interdiscount.





<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 7-->
<!----------------------------------------------------------------------->

## article_7_en

### {style="border: 0px; background: none"}

#### **How do Swiss consumers cope with masks? A view on online and on-site shopping**

<font size="2">October 21st, 2020</font><br>
<font size="2">Alexander Götz</font>

The introduction of compulsory wearing of masks on public transport (July 6, 2020) and for store visits in Zurich (August 27, 2020) was viewed critically at the beginning, as it could possibly slow down a growing post-lockdown consumer demand. This phenomenon has been studied both domestically and abroad with mixed results.  Following the nationwide introduction of increased protective measures (October 19, 2020), the question of the possible effects of the compulsory wearing of masks is even more pressing. This article therefore tries to add further evidence coming from Google search behavior.

The Global Economic Recovery Trackers of the [Financial Times](https://www.ft.com/content/272354f2-f970-4ae4-a8ae-848c4baf8f4a){target="_blank"}, which are based on high-frequency data like the trendEcon indicators, imply that the retail sector in some countries have returned to normal levels. However, if we look at the data on retail footfall, we see that on-site retail is still lagging behind to previous year’s levels (y/y). The year-to-year gap ranges from 20% (Italy, Sweden) to 60% (UK, US). In a [study](https://www.econstor.eu/bitstream/10419/218945/1/Compulsory_face_masks_Germany_5june2020.pdf){target="_blank"}, based on real-time mobility data, for Germany, economists conclude that a staggered introduction of mandatory masks has no significant impact on retail visits. The topic has also been taken up by local media [(NZZ, September 17, 2020)](https://www.nzz.ch/wirtschaft/coronavirus-maskenpflicht-geringe-einbussen-fuer-geschaefte-ld.1576918?mktcid=nled&mktcval=120&kid=nl120_2020-9-18&ga=&trco=){target="_blank"}. The article argues that the stricter mask obligation in Zurich has not led to losses in retail consumption (measured in number of card transactions) compared to Eastern or Central Switzerland. However, the regional analysis is limited to a period between August and September, without including previous year figures.

The trendEcon data allows a differentiated view of on-site and online retail trade. First of all, we see that the new expression "maskenpflicht" triggered great interest in both the canton and the entire country (dashed line). With the Federal Council's decision of 18 October 2020, search behaviour for "compulsory masks" has reached a new record high. But how has the obligation to wear a mask affected consumer spending in stationary retail stores? 

## Row

### {}
```{r masks_0_en}

article_7_CH <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_7_CH.csv") %>%
  ts_xts()
article_7_ZH <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_7_ZH.csv") %>%
  ts_xts()

ts_dygraphs(ts_c(
  `CH` = article_7_CH$maskenpflicht,
  `ZH` = article_7_ZH$maskenpflicht)) %>%
  dyRoller(rollPeriod = 4)%>% 
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("CH", label = "\"maskenpflicht\" searched in CH") %>%
  dySeries("ZH", label= "\"maskenpflicht\" searched in ZH only", strokePattern = "dashed") %>%
  dyEvent("2020-3-16", "Start Lockdown        ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Reopening - Phase I        ", labelLoc = "top") %>%
  dyEvent("2020-7-6", "Mask Measure CH - Public transport        ", labelLoc = "top") %>% 
  dyEvent("2020-8-27", "Mask Measure ZH - Retail        ", labelLoc = "top") %>% 
  dyEvent("2020-10-19", "Mask Measure CH - Retail        ", labelLoc = "top") %>% 
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {style="border: 0px; background: none"}

The search terms "öffnungszeiten" (opening hours), "shopping center" stand for consumption opportunities that are physically visited. The following time series show the search behavior in Switzerland and Zurich over the last two years. The term "öffnungszeiten" is hard to interpret. On the one hand, we could that that the pre-corona level has been reached again. The search behavior is even stronger compared to the same months last year. However, it is also possible that searchers might be looking for opening hours more often instead of standing in front of closed doors for safety reasons. The term "shopping center" was slightly less searched in Zurich after the compulsory wearing of masks was introduced, but it did pick up again during September. We observe that "shopping center" search queries have not yet reached the level of the previous year after a decline during the lockdown. It will be interesting to see what impact the second wave of infections will have on the typically strong Christmas season. However, the recent decision of the Federal Council has led to a visible downward trend throughout the country. The Federal Council has officially confirmed that the second wave has finally arrived in Switzerland. 

## Row

### {}
```{r mask_1_en}

ts_dygraphs(ts_c(
  `CH_ot` = article_7_CH[,1], 
  `CH_sc` = article_7_CH[,2],
  `ZH_ot` = article_7_ZH[,1],
  `ZH_sc` = article_7_ZH[,2])) %>%
  dyRoller(rollPeriod = 4)%>% 
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("CH_ot", label = "\"öffnungszeiten\" searched in CH") %>%
  dySeries("ZH_ot", label = "\"öffnungszeiten\" searched in ZH", strokePattern = "dashed") %>%
  dySeries("CH_sc", label = "\"shopping center\" searched in CH") %>%
  dySeries("ZH_sc", label = "\"shopping center\" searched in ZH", strokePattern = "dashed") %>%
  dyEvent("2020-3-16", "Start Lockdown        ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Reopening - Phase I        ", labelLoc = "top") %>%
  dyEvent("2020-7-6", "Mask Measure CH - Public transport        ", labelLoc = "top") %>% 
  dyEvent("2020-8-27", "Mask Measure ZH - Retail        ", labelLoc = "top") %>%
  dyEvent("2020-10-19", "Mask Measure CH - Retail        ", labelLoc = "top") %>% 
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {style="border: 0px; background: none"}
In the second figure, we look at the big names of Swiss online commerce, namely "galaxus", "coop at home" and "le store". Strikingly, the e-commerce giant Galaxus was able to improve its strong position during the lockdown. After a temporary explosion in search demand, a new level has now been reached above the previous year's figures. However, the online branches of Switzerland's largest retailers Coop and Migros show that the enormous peak during the lockdown was followed by a flattening off at the previous year's level. Nevertheless, the new security measures have again led to increased demand among all online retailers.

## Row

### {}
```{r mask_2_en}

ts_dygraphs(ts_c(
  article_7_CH$`coop at home`,
  article_7_CH$`le shop`,
  article_7_CH$galaxus)) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>%
  dyEvent("2020-3-16", "Start Lockdown        ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Reopening - Phase I        ", labelLoc = "top") %>%
  dyEvent("2020-7-6", "Mask Measure CH - Public transport        ", labelLoc = "top") %>% 
  dyEvent("2020-8-27", "Mask Measure ZH - Retail       ", labelLoc = "top") %>%
  dyEvent("2020-10-19", "Mask Measure CH - Retail        ", labelLoc = "top") %>% 
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {style="border: 0px; background: none"}
The data on Google search queries cannot directly identify an effect of the mask obligation; however, they do indicate a shift in non-food consumption habits from on-site to online, which can be shown in particular by a decline in food online retailers during the summer. However, increased purchases from home combined with a rather declining consumption ratio coud still imply that on-site consumption had not fully recovered. The renewed upturn in online consumption suggests that Swiss people are moving into the safety of their own homes rather than visiting stores.



<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 6-->
<!----------------------------------------------------------------------->

## article_6_en

### {style="border: 0px; background: none"}

#### **Football is back! But what about the fans?**

<font size="2">September 18th, 2020</font><br>
<font size="2">Alexander Götz</font>

This weekend marks the start of the new football season in Switzerland and Germany. Due to the Corona crisis, the Swiss Football League (SFL) has adjusted its match schedule for the 2020/2021 season. In addition to postponements, football fans in this country will also be affected by new regulations to which they will have to adapt. But are the fans ready fort hat and have they already bought their tickets?

Last month, the Swiss Football Association was already working on a draft for a [protection concept](https://www.football.ch/portaldata/27/resources/dokumente/diverses/Covid_Schutzkonzept_August2020_DE.pdf){target="_blank"} on how football clubs should treat their fans in a Corona-compliant manner. In addition to individual rules (only appear free of symptoms, keep your distance, wash your hands), guidelines that are the responsibility of the clubs must also be followed. For example, a maximum of 1000 in the stadium must not be exceeded until the end of October. According to the Federal Council's announcement of 12 August, from October onwards, in principle, more than 1000 people are permitted at major events. More importantly, however, the protection of citizens and thus also of stadium-goers is the responsibility of the cantons. In addition, it may be necessary to wear masks on the stadium grounds, which in turn depends on the various cantonal Covid-19 rules. Thus, depending on the stadium and the canton on which it is located, fans have to adapt to regional conditions.

It is complicated, indeed! If we use our trendEcon indicator for cultural events, we can see a level shift since the beginning of the year. It is striking that this shift is unique in the last four years. The indicator thus illustrates an uncertainty about the attendance of events in general. Although football can only remotely be associated with cultural events, this uncertainty also plays a role for fans.

The trendEcon data illustrate that the uncertainty regarding a stadium visit is high relative to recent years. The time series of the search term "Spielplan" (match schedule) reveals an interesting pattern: During major football tournaments (World and European Championships), the search behavior shoots up, while activity remains constant during the rest of the time. Only this year the level has dropped to an unprecedented low. If we look at the term "Saisonkarte"(season ticket), a similar picture emerges: Every second half of the year the demand for season tickets increases. This year, however, there has been a crash of this demand, which on average has settled at a lower level. Uncertainty about this year's fan joy has prompted, for instance, the Swiss champion BSC YB to temporarily suspend season ticket sales [(BSCYB News)](https://www.bscyb.ch/news?nID=12105){target="_blank"}. Such measures also contribute to the downward trend in season ticket sales.

We have also taken a look at the search terms "Fallzahlen" (incidents) and "Maskenpflicht" (mask requirement) and clearly see increased search activity for both terms. In particular, the term "Fallzahlen" has reached a new record level, which far exceeds the level of the first wave of infections in spring.

The data of our analysis illustrate the uncertainty of Swiss football fans. Due to these uncertainty about the second infection wave or possible new restrictions, we assume that the number of visitors to football stadiums will remain low. In general, this uncertainty affect they majority of Swiss people: How is the second wave developing? Is a mask required at public venues? Ultimately, these are questions that could have an impact not only on the sales of stadium tickets but also on general consumer spending.


## Row

### {}
```{r}

article_6 <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_6.csv") %>%
  ts_xts()

ts_dygraphs(article_6) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dyOptions(connectSeparatedPoints = TRUE) %>% 
  dySeries("maskenpflicht", strokeWidth = 2, strokePattern = "dashed") %>%
  dySeries("fallzahlen", strokeWidth = 2, strokePattern = "dashed") %>%
  dySeries("spielplan", strokeWidth = 2,drawPoints = FALSE) %>%
  dySeries("saisonkarte", strokeWidth = 2) %>%
  dyEvent("2020-3-16", "Lockdown     ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Phase I - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-5-11", "Phase II - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-6-8", "Phase III - Reopening     ", labelLoc = "top") %>%
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {}
```{r}

# Cultural Event indicator
cultural <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/social_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

cultural_2017 <- ts_data.frame(cultural["2017/2017-09-17"])%>% 
  mutate(time = as.Date(gsub("2017","2020",time))) %>% 
  ts_xts()

cultural_2018 <- ts_data.frame(cultural["2018/2018-09-17"])%>% 
  mutate(time = as.Date(gsub("2018","2020",time))) %>% 
  ts_xts()

cultural_2019 <- ts_data.frame(cultural["2019/2019-09-17"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

cultural_2020 <- ts_data.frame(cultural["2020/2020-09-17"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2017` = cultural_2017,
  `2018` = cultural_2018,
  `2019` = cultural_2019,
  `2020` = cultural_2020
)) %>%
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dySeries("2017", strokePattern = "dashed") %>%
  dySeries("2018", strokePattern = "dotdash") %>%
  dySeries("2019", strokePattern = "dashed") %>%
  dySeries("2020", strokePattern = NULL,  strokeWidth = 1.5) %>%
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = " Cultural Event trendecon index")


```


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 5-->
<!----------------------------------------------------------------------->

## article_5_en

### {style="border: 0px; background: none"}

#### **Culinary consumption patterns before, during and after the lockdown: Will the changes remain?**

<font size="2">September 3rd, 2020</font><br>
<font size="2">Alexander Götz</font>

On 27 August 2020, the State Secretariat for Economic Affairs (SECO) announced the historic 8.2% quarter-on-quarter decline in Swiss economic output during the second quarter of 2020. In their [economic note](https://www.seco.admin.ch/dam/seco/de/dokumente/Wirtschaft/Wirtschaftslage/VIP%20Quartalsschätzungen/konjunkturnotiz_2020_08_27.pdf.download.pdf/konjunkturnotiz_2020_08_27.pdf){target="_blank"}, SECO's economists explain that private consumption in particular has suffered an unprecedented slump. Past crises have shown that private consumption has saved the economy from worse developments, which are mostly fuelled by declining investments. During the current crisis, only changes in government expenditure have had a positive impact on the change in GDP. Foreign trade collapsed, as important trading partners of Switzerland were also affected by restrictions. Because private consumption represents the largest share of all GDP components, its fluctuations have a particularly strong impact on economic output. Therefore, the decline in consumption is a major contributor to the decline in GDP and has therefore been unable to fulfill its role as a guarantor of stability.

Ever since the outbreak of the pandemic and during the lockdown, [US economists](https://www.nber.org/papers/w26949){target="_blank"} have been speculating that current consumption habits could change not only in the short term but also in the medium or long term. In particular, the use of online shops for everyday shopping has been given a further boost by the lockdown restrictions, which could well ring in a turnaround in the retail sector. 

However, whether the composition of the consumer basket will change with shopping opportunities (e.g. via online shops instead of going to supermarkets) is another question. Whether and how the demand for goods changes can be investigated more closely by taking a look at specific consumer categories. In the following, we will look at consumption categories that are among the most everyday things in life: food.

With trendEcon we can take a closer look at the search queries for specific consumer goods that were presumably influenced by the pandemic and the lockdown. We have chosen the terms "restaurant" and "bar" as well as "recipe" and "sourdough" as search terms. 

The first pair of terms ("Restaurant" and "Bar"; dashed lines) reflects search queries related to going out. If we look at the temporal course of the search queries, it is apparent that the two terms were hardly googled during the lockdown and only regained their usual level towards the beginning of June 2020. Interestingly, we also see that the term "Restaurant" was searched for even more after than before the lockdown. On the one hand, this can be a compensatory effect, where people longed to enjoy a prepared meal instead of cooking themselves. But also a widespread uncertainty is conceivable; we are much more likely to check whether a restaurant is even open before we visit it. In the above-mentioned economic note, the SECO also reports compensatory effects in private consumption, but does not expect full compensation for the losses of the first half of the year.

The other terms ("Rezept" and "Sauerteig", solid lines) stand for activities that we associate with cooking at home. The development of search queries with "Rezept" shows that people typically look for recipes during holiday season in late December. However, the lockdown seems to have turned restaurant goers into cooks. Surprisingly, Swiss people have also taken time for more complex procedures such as the cultivation of sourdough [(NZZ, June 2020)](https://www.nzz.ch/zuerich/sauerteig-eine-ode-an-das-tamagotchi-der-corona-krise-ld.1558248){target="_blank"}. The time series on the search behavior for "Sauerteig" documents a huge hype between March and May, which came to an abrupt end after the first easing of the lockdown rules, which could be due to the fact that employees left their home offices again. 

A look at the current state shows that the search terms shown have reached old levels again. Concerns about the effects of the second infection wave or job security may, however, continue to affect consumer behavior in the coming weeks. Therefore, we will see whether private consumption will be able to stabilize the declining economic output in the coming quarter. We are skeptical, however, whether sourdough will be part of this near future.


## Row

### {}
```{r}

article_3 <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_3.csv") %>%
  ts_xts()

ts_dygraphs(article_3) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("Restaurant", strokeWidth = 2, strokePattern = "dashed") %>%
  dySeries("Bar", strokeWidth = 2, strokePattern = "dashed") %>%
  dyEvent("2020-3-16", "Lockdown     ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Phase I - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-5-11", "Phase II - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-6-8", "Phase III - Reopening     ", labelLoc = "top") %>%
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```

<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 4-->
<!----------------------------------------------------------------------->


## article_4_en

### {style="border: 0px; background: none"}

#### --------------------------------------------

#### **Back to normal or permanent shifts in demand?**

<font size="2">02. September 2020</font><br>
<font size="2">Stefan Legge</font>

Life changed dramatically for people in Switzerland in the spring of 2020 when the Federal Council announced the so-called lock-down in mid-March. Not being able to go to restaurants, bars, or shopping malls, Swiss people found new ways to enjoy their leisure time.

Concerning food, two activities stood out: baking bread and ordering food online. The former was so widespread that The Economist [wrote about it in July](https://www.economist.com/leaders/2020/07/09/sourdough-economics-no-need-to-knead){target="_blank"}. As the British magazine pointed out, however, when the pandemic and economic downturn is over, people should leave bread-making to the experts and focus on bread-winning with their normal jobs. Similarly, when restaurants opened again many people quickly abandoned food delivery and went out again.

This raises the question whether the Covid-19 shock led only to short-term adjustments in how people spend their leisure time. Alternatively, do we find any (thus far) lasting changes in consumer demand?

Using trendEcon, we see how Google search frequencies evolved in the past weeks, months, and years. This allows us to test whether Swiss consumers shifted preferences only temporarily or permanently. In the figure below, we illustrate the results for the keywords “Brot backen” (baking bread), “Essen bestellen” (order food), “Netflix”, as well as a group of words related to gardening and home improvement.

## Row

### {}
```{r art_4_0_en}

blog_ar_4 <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_4.csv") %>%
  ts_xts()

ts_dygraphs(blog_ar_4) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dyAxis("x", drawGrid = FALSE) %>% 
  dySeries("Netflix", strokePattern = NULL)%>% 
  dySeries("Essen bestellen", strokePattern = "dashed") %>% 
  dySeries("Brot backen", strokePattern = "dotdash") %>% 
  dyLegend(width = 500) %>% 
  dyHighlight(highlightCircleSize = 3, 
              highlightSeriesBackgroundAlpha = 0.7,
              hideOnMouseOut = TRUE)
```

## Row

### {style="border: 0px; background: none"}

For some of the keywords the data indicate a short-term boom during Covid-19. Interest in baking bread or food delivery surged rapidly during the lock-down but plummeted equally fast with the first easing of restrictions. Meanwhile, searches for gardening-related terms remains at an elevated level compared to pre-Corona times.The Covid-19 crisis has caused some dramatic changes in people’s lives and consumption patterns. It seems plausible that people will stick to some of these new habits, such as ordering food online or enjoying their free time gardening.

If that happens companies will face a different consumer demand in the future. This has first-order implications for investment decisions. Making them in anticipation of a sustained boom should be based on a profound understanding of the shifts in demand. The data provided by trendEcon help by offering valuable insights into consumers’ minds.

## Row

### {}
```{r art_4_1_en}

food <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/fooddelivery_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

food_2018 <- ts_data.frame(food["2018/2018-09-01"])%>% 
  mutate(time = as.Date(gsub("2018","2020",time))) %>% 
  ts_xts()

food_2019 <- ts_data.frame(food["2019/2019-09-01"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

food_2020 <- ts_data.frame(food["2020/2020-09-01"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2018` = food_2018,
  `2019` = food_2019,
  `2020` = food_2020
)) %>%
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dySeries("2018", strokePattern = "dotdash") %>%
  dySeries("2019", strokePattern = "dashed") %>%
  dySeries("2020", strokePattern = NULL) %>%
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = "Food delivery trendecon index")

```

## Row

### {}
```{r art_4_2_en}

garden <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/garden_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

garden_2018 <- ts_data.frame(garden["2018/2018-09-01"])%>% 
  mutate(time = as.Date(gsub("2018","2020",time))) %>% 
  ts_xts()

garden_2019 <- ts_data.frame(garden["2019/2019-09-01"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

garden_2020 <- ts_data.frame(garden["2020/2020-09-01"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2018` = garden_2018,
  `2019` = garden_2019,
  `2020` = garden_2020
)) %>%
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dySeries("2018", strokePattern = "dotdash") %>%
  dySeries("2019", strokePattern = "dashed") %>%
  dySeries("2020", strokePattern = NULL) %>%
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = "Gardening and home improvement trendecon index")

```


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 3a-->
<!----------------------------------------------------------------------->

## article_3a_en

### {style="border: 0px; background: none"}

#### --------------------------------------------

#### **Still a long way to go**

<font size="2">August 26th, 2020</font><br>
<font size="2">Stefan Legge</font>

Many of the tasks that people need to get done have not changed in centuries: getting food, finding a comfortable place to sleep, treating injuries and illnesses, or getting from one place to another. Influential business theorists Clayton M. Christensen built a theory of the [jobs to be done](https://hbr.org/2016/09/know-your-customers-jobs-to-be-done){target="_blank"} based on this fact. His key observation was that the tools and procedures people employ to get these jobs done change much more frequently than the jobs themselves.

Concerning mobility, people changed their primary mode of transportation whenever new technologies – the train, the car, the airplane – allowed and incentivized them to do so. Most recently, we witnessed another reason why people changed the way they got from A to B: the Covid-19 pandemic made some forms of transportation less attractive. In addition, due to health concerns many people travelled far less. 

Current data from KOF indicate that the average distance travelled (illustrated by the [mobility](https://kofdata.netlify.app/#/keys?dataset=ch.kof.mobind){target="_blank"} index) has largely recovered from its low point at the end of March. This allows us to ask interesting questions: Has the pandemic led to sustained changes in the modes of transportation? Do people continue to use bikes and cars instead of public transport?

The data provided by trendEcon shed light on this.We observe how Google search frequencies evolved in the recent past and can compare it to levels in 2019 or 2018. This enables us to test whether Swiss citizens shifted preferences on mobility only temporarily or permanently. In the figure below, we illustrate the results for the keywords “Velo kaufen” (buying a bike), “Auto kaufen” (buying a car), “Bus Ticket”,as well as “Zugticket” (train ticket). In addition, we plot our mobility index together with the one from KOF.

The data indicate a clear short-term impact of Covid-19: interest in bikes peaked while searches for public transport plummeted. More interesting are the lasting consequences of this shock. While still early – the pandemic is not over – we continue to see an elevated interest in bikes. It remains to be seen whether this prevails in the coming months. Similarly, the negative shock to public transportation (buses and trains) still lasts with public interest reduced substantially compared to pre-Corona times.

Covid-19 caused some dramatic changes in people’s lives and mobility preferences.Data provided by trendEconoffers up-to-date insights into key mobility trends.

## Row

### {}
```{r art_3a_mob_1}

blog_ar_3_a <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_3_a.csv") %>%
  ts_xts()

ts_dygraphs(blog_ar_3_a[,1:2]  %>%
              ts_frequency("month")) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dyAxis("x", drawGrid = FALSE) %>% 
  dySeries("Auto kaufen", strokePattern = "dashed") %>% 
  dyLegend(width = 500) %>% 
  dyHighlight(highlightCircleSize = 3, 
              highlightSeriesBackgroundAlpha = 0.7,
              hideOnMouseOut = TRUE)
```

## Row

### {}
```{r art_3a_mob_2}

blog_ar_3_a <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_3_a.csv") %>%
  ts_xts()

ts_dygraphs(blog_ar_3_a[,3:4]  %>%
              ts_frequency("month")) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dyAxis("x", drawGrid = FALSE) %>% 
  dySeries("Zugticket", strokePattern = "dashed") %>% 
  dyLegend(width = 500) %>% 
  dyHighlight(highlightCircleSize = 3, 
              highlightSeriesBackgroundAlpha = 0.7,
              hideOnMouseOut = TRUE)

```

## Row

### {}
```{r art_3a_mob_3}

kof_mob <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_3_a_mobility_kof.csv") %>%
  ts_xts()

mobility_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/mobility_sa.csv",index.column = 1))
mobility_trendecon <- as.xts(mobility_sa["2020-01-07/2020-08-24"])
mobility_trendecon_r <- (mobility_trendecon-min(mobility_trendecon))/(max(mobility_trendecon)-min(mobility_trendecon))

mobility <- cbind(kof_mob,mobility_trendecon_r)

ts_dygraphs(mobility) %>%
  dyAxis("x", drawGrid = FALSE)%>%
  dyAxis("y", label = "rescaled index") %>% 
  dySeries("value", label = "KOF mobility index") %>%
  dySeries("mobility_trendecon_r", label = "trendecon mobility index", strokePattern = "dashed") %>%
  dyEvent("2020-3-16", "Lockdown    ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Reopening - Phase I    ", labelLoc = "top") %>%
  dyEvent("2020-5-11", "Reopening - Phase II    ", labelLoc = "top") %>%
  dyEvent("2020-6-8", "Reopening - Phase III    ", labelLoc = "top") %>% 
  dyLegend(width = 500) %>% 
  dyHighlight(highlightCircleSize = 3, 
              highlightSeriesBackgroundAlpha = 0.7,
              hideOnMouseOut = TRUE)

```


<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 2-->
<!----------------------------------------------------------------------->

## article_2_en

### {style="border: 0px; background: none"}

#### --------------------------------------------

#### **Large events will be allowed soon – but will people show up?**

<font size="2">August 24th, 2020</font><br>
<font size="2">Stefan Legge</font>

On August 12, 2020 the Federal Council of Switzerland [announced](https://www.srf.ch/news/schweiz/grossanlaesse-masken-kredite-das-hat-der-bundesrat-entschieden){target="_blank"} that starting in October large events with more than one thousand participants will be allowed again. This marked another round of easing the COVID-19 related restrictions imposed in March. Many companies, sports clubs, and event organizers were relieved to finally see light at the end of the tunnel.


But just because large events are allowed does not mean that people will actually attend them. The number of daily new COVID-19 cases has been on an upward trend for weeks. Many - but not all – people in Switzerland still try to avoid large gatherings. A [U.S. study shows](https://www.nber.org/papers/w27650){target="_blank"} that reopening restaurants after lock-downs lead customers to believe that it was safe to eat out again. Similarly, allowing large events may send a signal of safety. So, has the recent announcement led individuals to change their mind?


Using trendEcon, we can see how Google search frequencies evolved in the past days, weeks, or months. As keywords we use “Festival”, “Tickets kaufen” (buy tickets), “Hallenstadion” (a multi-purpose facility in Zurich), “Letzigrund” (stadium in Zurich), as well as “Konzert” (concert).
For none of the keywords do the data indicate a positive impact of the recent announcement. It appears that Swiss people have not rushed to find events and buy tickets. There could be many reasons for this muted response: the population is still concerned about the virus (the number of searches for “corona” or “corona symptoms” remains stable at a high level) and the perceived economic situation continues to be worse than before the pandemic hit in late February. Furthermore, organizers of large events still hesitate to plan for 2020. The Hallenstadion Zurich currently lists only seven events for the rest of the year.
The coming weeks will show whether the demand for large events increases as Switzerland comes closer to the October relaunch of large events. If not, that light at the end of the tunnel might not be too bright after all.

## Row

### {}
```{r}

article_2 <- read.csv("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/article_2.csv") %>%
  ts_xts()

ts_dygraphs(article_2) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("Hallenstadion", strokeWidth = 2, strokePattern = "dashed") %>%
  dySeries("Festival",strokeWidth = 1, strokePattern = "dashed") %>%
  dySeries("Konzert",drawPoints = TRUE) %>%
  dyEvent("2020-3-16", "Lockdown     ", labelLoc = "top") %>%
  dyEvent("2020-4-27", "Phase I - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-5-11", "Phase II - Reopening     ", labelLoc = "top") %>%
  dyEvent("2020-6-8", "Phase III - Reopening     ", labelLoc = "top") %>%
  dyLegend(width = 500) %>%
  dyAxis("x", drawGrid = FALSE)
```




<!----------------------------------------------------------------------->
<!----------------------------------------BLOG PAGE ENGLISH / Article 1-->
<!----------------------------------------------------------------------->

## article_1_en

### {style="border: 0px; background: none"}

#### --------------------------------------------

#### **How is the Swiss economy doing today?**

##### trendEcon offers new insights

<font size="2">May 25th, 2020</font><br>

The first half of 2020 can already be regarded as historic. Seldom before have economies shrunkas fast in such a short time. As a result of COVID-19 and the related government measures, unemployment figures are rising rapidly practically everywhere. Economic performance measured by gross domestic product (GDP) is falling more sharply than we have seen in decades. However, there is still vast uncertainty about how dramatic the economic slump will be and how quickly economies will recover from the crisis.

In Switzerland, annual GDP is expected to fall by around six percent [(Seco, April 2020)](https://www.seco.admin.ch/seco/de/home/wirtschaftslage---wirtschaftspolitik/Wirtschaftslage/konjunkturprognosen.html){target="_blank"}. However, this will not affect all sectors of the economy equally. Restaurants and airports are himuch harder hit than supermarkets or the pharmaceutical industry, for example. While the extremes are quite obvious, many questions remain open. 

How quickly, for example, will the demand for durable goods rise again? In recessions, consumers save money, reducing spending especially on clothing, furniture, or cars. Spending in these areas is easier to postpone, which is why these sectors are very pro-cyclical: In a recession they suffer particularly - and with them the advertising industry and, in the next instance, newspapers, which sell fewer advertisements. Consequently, the demand for clothing or cars is also important for many other industries via second- and third-round effects.

The high level of uncertainty poses a problem for both politicians and companies. How much government support is needed and where is it most needed? When will companies again face increasing demand and thus turnover?

Data can help us to improvethe answersto such questions. However, in many case, data first have to be prepared and graphically illustrated. The new platform [trendEcon.org](#home) created by us aims at exactly this. Every day, Swiss people search Google for countless keywords. Via [Google Trends](https://trends.google.de/trends/?geo=CH){target="_blank"}, anyone can see which keywords are currently being searched for very frequently. A look at the terms "WC Papier" (toilet paper) and "Rezession” (recession) is illustrative:

## Row

### {}
```{r}
wc_papier_ts <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/wc_papier.csv",index.column = 1))

rezession_ts <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/media-content/master/data_examples/rezession.csv",index.column = 1))

ts_dygraphs(ts_c(
  `WC Papier` = wc_papier_ts,
  `Rezession` = rezession_ts
)) %>%
  dyAxis("y", label = "Hits (index from Google trends)") %>% 
  dySeries("WC Papier", strokePattern = "dashed") %>%
  dyAxis("x", drawGrid = FALSE)
```

## Row

### {style="border: 0px; background: none"}

It can be clearly seen here how from the second week of March onwards the number of search requests for "recession" increased. We also observe the large number of people searching for toilet paper on the Internet in mid-March due to a short-term shortage. The concern about toilet paper quickly disappeared, but the topic of recession is still very present.

While such examples are very illustrative, they also highlight some of the problems: Which search terms are actually relevant and how can several terms be combined? How can the data be presented in a clean and comparable way? What are useful benchmarks? We at **trendEcon** try to address these aspects by selecting the most suitable search terms from a multitude of possible search terms and preparing the data from January 2006 onwards. The latter includes among others a seasonal adjustment as well as the consideration of public holidays.

As a result, **trendEcon** currently shows not only a crisis index but also the development over time for several sectors. Our main indicator "Perceived Economic Situation" is based on the keywords "economic crisis", "short-time work", "unemployed" and "insolvency". The data based on this provides a picture of the extent to which people in Switzerland are concerned about economic development. The more frequently the four terms are searched for, the worse the assessment of the current situation. The slump from the end of February onwards and the low point shortly after the Federal Council's decisions of March 16, 2020 are clearly visible in the graph:


## Row {.tabset .tabset-fade}

### Perceived Economic Situation (daily)

```{r}

trendecon_all_sa <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

dygraph(trendecon_all_sa,group = "keywords")%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("value", label = "Index") %>%
  dyEvent("2020-3-16", "Lockdown", labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r}

data_monthly <- trendecon_all_sa %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Perceived Economic Situation` = data_monthly
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The indicator for *Perceived Economic Situation* includes search terms that reflect people’s worries about the economy. For instance, people then google “economic crisis” (Wirtschaftskrise).

###### Keywords

- wirtschaftskrise
- kurzarbeit
- arbeitslos
- insolvenz

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv){target="_blank"}

## Row

### {style="border: 0px; background: none"}

It is also noticeable that sentiment has already brightened considerably again - although the indicator is still below the long-term level. As comparison, one can use the data from 2019 to see the striking differ-ence:

## Row

### {}
```{r}
trendecon_all_sa <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

PEI_2019 <- ts_data.frame(trendecon_all_sa["2019/2019-05-25"])%>% 
  mutate(time = as.Date(gsub("2019","2020",time))) %>% 
  ts_xts()

PEI_2020 <- ts_data.frame(trendecon_all_sa["2020/2020-05-25"]) %>% 
  ts_xts()

dygraph(ts_c(
  `2019` = PEI_2019,
  `2020` = PEI_2020
)) %>%
  dyAxis("x",valueFormatter=JS(getMonthDay), axisLabelFormatter=JS(getMonth)) %>% 
  dyAxis("x", drawGrid = FALSE) %>% 
  dyAxis("y", label = "Perceived Economic Situation")
```

## Row

### {style="border: 0px; background: none"}

In addition to the overall economic analysis, **trendEcon** also offers a range of sector-specific indicators. The strong and continuing slump in the travel industry is a confirmation of the quality of the data. Search queries for"city trip", "book flight" or "cheap flights" (note: we use the German words) are still rare compared to the pre-Corona period:

## Row {.tabset .tabset-fade}

### Travel Abroad
```{r}
travel_sa <- as.xts(zoo::read.csv.zoo("https://raw.githubusercontent.com/trendecon/data/master/data/ch/travel_sa.csv",index.column = 1))

dygraph(travel_sa)%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("V1", label = "index") %>%
  dyEvent("2020-3-16", "Lockdown", labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Info

###### Description

The category *Travel Abroad* includes search terms used to book flights and holidays.

###### Keywords

- städtetrip
- flug buchen
- günstige flüge

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/ch/travel_sa.csv){target="_blank"}

## Row

### {style="border: 0px; background: none"}

We see a similar and continuing slump in cultural events. In contrast, demand for food deliveries or DIY stores is at a (positive) record level.

In summary, **trendEcon** offers a platform for daily updated information on the state of the Swiss economy. In the coming weeks, we will be adding further search terms and (sub-) indicators in order to constantly increase the amount of information available. In addition, we are constantly testing the usefulness of our data for forecasting economically relevant variables. All data are freely available for [Download](https://github.com/trendecon/data/tree/master/data/) and the code will be publicly available soon.

<!----------------------------------------------------------------------->
<!-------------------------------------------------------- METHOD PAGE -->
<!----------------------------------------------------------------------->
# <font size="3">Method</font> {data-icon="fa-file-contract"}

### {style="border: 0px; background: none"}

#### **Related research**

Other researchers have explored using Google Trends for economic forecasts. [Ferrara & Simoni (2019)](https://drive.google.com/file/d/1KVcsn5aFCogqFiP4uormtg1GEnT7A4W9/view){target="_blank"} argue that Google data bring useful information for GDP nowcasting for the four first weeks of the quarter when macroeconomic information is lacking. [Joni Heikkinen (2019)](https://jyx.jyu.fi/bitstream/handle/123456789/66363/URN%3ANBN%3Afi%3Ajyu-201911144867.pdf?sequence=1){target="_blank"} applies the idea of nowcasting economic growth using Google Trends data to Germany and Finland. [Narita and Yin (2018)](https://ideas.repec.org/p/imf/imfwpa/18-286.html){target="_blank"} have done so for low-income developing countries and Castelnuovo and Tran (2017) for the United States and Australia.

Specifically for consumption, [Woo and Owen (2019)](https://onlinelibrary.wiley.com/doi/full/10.1002/for.2559){target="_blank"} document that Google Trends-augmented models provide additional information about consumption over and above survey-based consumer sentiment indicators.

Regarding key words that reflect economic sentiments and uncertainty, we build upon prior work by [Baker, Bloom, and Davis (2016)](https://academic.oup.com/qje/article/131/4/1593/2468873){target="_blank"}.

#### **Related indicators**

Since 1972, SECO conducts the [Consumer Sentiment](https://www.seco.admin.ch/seco/en/home/wirtschaftslage---wirtschaftspolitik/Wirtschaftslage/Konsumentenstimmung.html){target="_blank"} survey on a quarterly basis (in January, April, July and October). Its aim is to compile data from around 1'000 households on subjective assessments and expectations with respect to the general state of the economy, the consumers' financial situation, the development of prices, job security and so forth. Similar indicators on consumer confidence based on surveys include the [OECD's Consumer Confidence Index](https://data.oecd.org/leadind/consumer-confidence-index-cci.htm){target="_blank"}, the [University of Michigan's Consumer Sentiment Index](https://data.sca.isr.umich.edu/){target="_blank"}, the [Economic Policy Uncertainty Index](http://www.policyuncertainty.com/){target="_blank"}, or [CNN's Fear and Greed Index](https://money.cnn.com/data/fear-and-greed/){target="_blank"}.

#### **Methods**

##### **Sampling issues in a small market**

If you query Google Trends for a search term, e.g., *insolvenz*, the result is based on a subsample of all search [results](https://trends.google.com/trends/explore?date=today%201-m&geo=CH&q=insolvenz){target="_blank"}.

For a small country like Switzerland, these results may differ quite dramatically from sample to sample.

In order to alleviate the problem, we usually draw 12  or more samples for each series (keyword and frequency). We force Google to re-sample by choosing a different time window.

##### **Creating long daily series**

Google search results are available on a daily, weekly or monthly frequency. As with individual samples, querying Google at a different frequency will lead to substantially different results.

Our goal is to produce long daily time series, ideally from 2006.
This is mostly because we want to use the financial crisis of 2008 and 2009 as a benchmark for the Covid-19 crisis. However, Google does not provide daily or weekly data for such a long time period. We circumvent the problem by applying a moving window of daily and weekly queries over the whole time period.

Since the daily, weekly and monthly series are still very different, we want to combine them into a single daily series.

Our next steps are based on the following assumptions:

- Monthly data catches the long term trend in search activity in the most accurate way.

- Weekly data is best to analyze the searches over the medium term, i.e., over a few months.

- Daily data is best to analyze short term behavior over a few days and weeks.

With this in mind, we apply the following methodology. In a first step, we "bend" the daily series to the weekly values, by applying a variant of the [Chow-Lin (1971)](https://doi.org/10.2307/1928739){target="_blank"} method. This preserves the movement of the daily series and ensures that weekly averages are identical to the original weekly series.

In a second step, we bend the adjusted weekly series from the first step to the monthly values, using the same method again. This produces a series that maintains most of the movement of the daily and the weekly series, but has the same monthly averages as the monthly series. This series are used for further processing described in the subsequent sections.

[Literature](https://journal.r-project.org/archive/2013/RJ-2013-028/index.html){target="_blank"}

##### **Seasonal adjustment**

Daily series have multiple seasonalities:

- There is *weekly seasonality* : Search activities for business related activities may lower during the weekend.

- There is *monthly seasonality* : If salaries are paid by the end of the month, some kind of shopping may be more likely to occur afterwards.

- There is *yearly seasonality* : Flip flop is an unpopular search term in Winter, while Christmas is rarely looked up in Summer.

- Finally, there are *irregular holidays* that occur at a different dates each year, such as Easter.

We use the [Prophet procedure](https://peerj.com/preprints/3190/){target="_blank"} for estimating an additive model where non-linear
trends are fit with yearly and weekly seasonality and the holiday effects. The
procedure is fully automated and easy to use, but has a few drawbacks. It does
not model monthly seasonality and all the seasonal effects are assumed to be constant over time.

##### **Aggregation of indicators**

In a final step, we use principal component analysis (PCA) to extract the common signal from a group of seasonally adjusted, daily time series. The idea of PCA is to identify several principal components that summarize most of the variance in the data. We then use the first principal component as our index. We manually checked the factor loadings and scores and adjusted the variable selection if needed.

##### **Find out more in our working paper**

[Constructing Daily Economic Sentiment Indices Based on Google Trends](https://drive.google.com/file/d/12ssYVfF0Kdp0pQXZgFtKetGJmGGH2KEd/view?usp=sharing){target="_blank"}.

#### **Access our data**

The data can be accessed [here](https://github.com/trendecon/data){target="_blank"}. Our indicator data is public and freely available under license Attribution 4.0 International [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/){target="_blank"}.
This means that you can remix, adapt, and build upon this work non-commercially, as long as you credit us and license your new creations under the identical terms.

<!----------------------------------------------------------------------->
<!---------------------------------------------------- Other countries -->
<!----------------------------------------------------------------------->

# <font size="3">Austria</font> {data-navmenu="Other countries"}

#### Austria

## Row {.tabset .tabset-fade}

### Perceived Economic Situation (daily)

```{r main_index_at}

trendecon_all_sa_at <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/at/trendecon_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

dygraph(trendecon_all_sa_at,group = "keywords")%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("value", label = "Index") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r main_index_monthly_at}

data_monthly_at <- trendecon_all_sa_at %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Perceived Economic Situation` = data_monthly_at
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The indicator for *Perceived Economic Situation* includes search terms that reflect people’s worries about the economy. For instance, people then google “economic crisis” (Wirtschaftskrise).

###### Keywords

- wirtschaftskrise
- kurzarbeit
- arbeitslos
- insolvenz

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/at/trendecon_sa.csv){target="_blank"}

# <font size="3">Germany</font> {data-navmenu="Other countries"}

<!----------------------------------------------------------------------->
<!---------------------------------------------------- Germany ---------->
<!----------------------------------------------------------------------->

#### Germany

## Row {.tabset .tabset-fade}

### Perceived Economic Situation (daily)

```{r main_index_de}

trendecon_all_sa_de <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/de/trendecon_sa.csv") %>%
  select(time,value) %>%
  ts_xts()

dygraph(trendecon_all_sa_de,group = "keywords")%>%
  dyAxis("x", drawGrid = FALSE)%>%
  dySeries("value", label = "Index") %>%
  dyRangeSelector(dateWindow = c("2020-01-01", today))
```

### Monthly

```{r main_index_monthly_de}

data_monthly_de <- trendecon_all_sa_de %>%
  ts_frequency("month")

ts_dygraphs(ts_c(
  `Perceived Economic Situation` = data_monthly_de
)) %>%
  dyRangeSelector()
```

### Info

###### Description

The indicator for *Perceived Economic Situation* includes search terms that reflect people’s worries about the economy. For instance, people then google “economic crisis” (Wirtschaftskrise).

###### Keywords

- wirtschaftskrise
- kurzarbeit
- arbeitslos
- insolvenz

[Download data](https://raw.githubusercontent.com/trendecon/data/master/data/de/trendecon_sa.csv){target="_blank"}


<!----------------------------------------------------------------------->
<!--------------------------------------------------------- ABOUT PAGE -->
<!----------------------------------------------------------------------->
# <font size="3">About this project</font> {data-icon="fa-users"}

### {style="border: 0px; background: none"}

#### **About this project**

This project was born at the end of March 2020 as economists were in dire need to obtain timely data to estimate the impact of the Covid-19 pandemic on the Swiss economy.

It started as a collaboration between economists working at the data consulting company [cynkra](https://www.cynkra.com/#){target="_blank"}, [KOF Swiss Economic Institute](https://kof.ethz.ch/en/){target="_blank"}, the economic forecast division of the State Secretariat for Economic Affairs ([SECO](https://www.seco.admin.ch/seco/en/home/wirtschaftslage---wirtschaftspolitik/Wirtschaftslage/konjunkturprognosen.html){target="_blank"}), the Swiss Federation of Trade Unions ([SGB](https://www.sgb.ch/aktuell){target="_blank"}) and the [University of St. Gallen](https://siaw.unisg.ch/){target="_blank"}.

We will continue to work on this project along the way and possibly add further indicators.

#### **Contributors**

* [Angelica Becerra](https://www.linkedin.com/in/angelicambg/){target="_blank"} (Statistician and data scientist, ETH KOF)
* [Vera Z. Eichenauer](https://sites.google.com/view/vera-eichenauer/home){target="_blank"} (Economist, ETH KOF)
* [Alexander Götz](https://www.linkedin.com/in/a1exandergoetz/){target="_blank"} (Economist, ETH GESS)
* Ronald Indergand (Head of Short Term Economic Analyses, SECO)
* [Stefan Legge](https://sites.google.com/view/stefanlegge){target="_blank"} (Economist, University of St.Gallen)
* [Isabel Martinez](https://sites.google.com/view/isabelzmartinez/home){target="_blank"} (Economist, ETH KOF, formerly SGB)
* Nina Mühlebach (Economist, ETH KOF)
* Furkan Oguz (Economist, ETH KOF)
* [Christoph Sax](https://www.cynkra.com/about.html){target="_blank"} (Economist and data scientist, cynkra)
* Kristina Schuepbach (Economist, SGB and University of Bern)
* Severin Thöni (Programmer, ETH KOF)
* [Uwe Thümmel](http://uwethuemmel.com){target="_blank"} (Economist, University of Zurich)

#### **Contact**

#### trendecon@gmail.com

<!----------------------------------------------------------------------->
<!----------------------------------------------------------- FAQ PAGE -->
<!----------------------------------------------------------------------->
# <font size="3">FAQ</font> {data-icon="fa-question"}

#### **FAQ**

###### Why are these indicators different than just using Google Trends?

On [Google Trends](https://trends.google.de/trends/?geo=CH){target="_blank"}, you will find series based on a random sample of Google searches conducted in Switzerland. Depending on the time frame you choose, Google returns daily, weekly, or monthly data. We usually downloaded the data 12 times or more times to construct long-run data with a daily frequency. We further adjust the data for seasonal patterns in searches. It is not surprising that searches for gardening are higher in spring. To make meaningful comparisons over time, these seasonal patterns are removed. Finally, our indicators are not based on one single keyword but several keywords are aggregated into one indicator. See [Method](#method) for further details.

###### Why did you use exactly these few keywords?

We carefully selected keywords based on expected consumer search behavior. For each indicator, we list the keywords next to the figure in the mini-tab *Info*.

We try to stick to those keywords that are most likely to reflect the intention to consume certain types of goods and services rather than just having an interest in learning more about them.

You'll probably still find that not every keyword that one might think of went into our indicator. This is due to the following reasons: First, to ensure privacy, [Google Trends](https://trends.google.de/trends/?geo=CH){target="_blank"} does not return search trends based on a small number of searches. Some keywords of interest are therefore censored and return a lot of zeros. Second, other keywords do not show any significant changes over time that coincide with economic activity or changes in demand. These keywords contain no relevant information to go into our indicators. Finally, more is not always better. We use those keywords that correlate strongest with real economic activity.

###### Why do you use only German keywords?

German is the main language of 63% of the population in Switzerland. Search trends on Google are likely to be representative for the whole economy. Indeed, this is what we find if we compare our indicators to the existing target indicators like consumer sentiment. Due to Google's privacy restrictions, searches in French and Italian within Switzerland are more often censored than German ones. If keywords are censored, Google replaces observations with a zero and we cannot use the keyword. This is another reason why we opt for using names of stores or brands: these do not depend on the language preferred by the Google user.

###### How reliable are these indicators?

We put a lot of effort into constructing daily, seasonally adjusted indicators that correlate with existing economic indicators. They can be used to say something about the evolution of demand for certain consumption categories. However, they remain indicators. We do not measure true economic activity as in number of T-shirts sold on a specific day or money spent on gardening equipment. Also note that this is an experiment in real time. If the correlation between search behavior and consumer demand changes, our indicators may become better or get worse in tracking consumer demand.

###### What do these indicators tell us?

The indicators are based on search volumes for chosen keywords. However, the number of searches is unknown, as Google does not share this information to protect users' privacy. Depending on the indicator, you can interpret the indicators as *relative changes over time* in interest, concerns, or demand for certain topics, goods, or services. We list the keywords that went into the indicator to facilitate interpretation in the mini-tab *Info* next to the figure representing each indicator.

The more technical and quantitative interpretation is as follows: all series are normalized such that the long-term equals zero and the standard deviation is one. E.g., an index value of 2 means that search volume for this item is two standard deviations above the average.

###### What do these indicators not tell us?

The indicators cannot quantify changes in GDP or total consumer demand. Given how the indicators are constructed, it is also impossible to infer growth rates. Google does not share the total number of searches to protect users' privacy makes it impossible to say something about absolute changes in search volumes.

###### How can I work with the data?

The data can be accessed [here](https://github.com/trendecon/data){target="_blank"}. Our indicator data is public and freely available under license Attribution 4.0 International [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/){target="_blank"}.
This means that you can remix, adapt, and build upon this work non-commercially, as long as you credit us and license your new creations under the identical terms.

## Row {.tabset .tabset-fade data-height=100}

```{r echo = FALSE}


```

```{r echo = FALSE}


```


